\setlength{\leftskip}{0.0in}
\setlength{\parindent}{0.5in}
\clearpage
\section{Appendices}\label{appendices}

\section{Appendix A: Moral Scenarios}\label{appendix-a-moral-scenarios}

\subsection{Heinz}\label{heinz}

In Europe, a woman was near death from a very bad disease, a special
kind of cancer. There was one drug that the doctors thought might save
her. It was a form of radium for which a druggist was charging ten times
what the drug cost him to make. The sick woman's husband, Heinz, went to
everyone he knew to borrow the money, but he could only get together
about half of what it cost. He told the druggist that his wife was
dying, and asked him to sell it cheaper or let him pay later. But the
druggist said, ``No, I discovered the drug and I'm going to make money
from it.'' So, Heinz got desperate and broke into the man's store to
steal the drug for his wife. The druggist had Heinz arrested and charged
(Haidt et al., 2000).

\subsection{Trolley}\label{trolley}

A Trolley is hurtling down a track towards five people. It will kill
them all on impact. Paul is on a bridge under which it will pass. He can
stop it by putting something very heavy in front of it. As it happens,
there is a very fat man next to him -- Paul's only way to stop the
trolley is to push him over the bridge and onto the track, killing him
to save five. Paul decides to push the man (adapted from Greene et al.,
2001).

\subsection{Cannibal (original)}\label{cannibal-original}

Jennifer works in a medical school pathology lab as a research
assistant. The lab prepares human cadavers that are used to teach
medical students about anatomy. The cadavers come from people who had
donated their body to science for research. One night Jennifer is
leaving the lab when she sees a body that is going to be discarded the
next day. Jennifer was a vegetarian, for moral reasons. She thought it
was wrong to kill animals for food. But then, when she saw a body about
to be cremated, she thought it was irrational to waste perfectly edible
meat. So she cut off a piece of flesh, and took it home and cooked it.
The person had died recently of a heart attack, and she cooked the meat
thoroughly, so there was no risk of disease (Haidt et al., 2000).

\subsection{Cannibal (revised)}\label{cannibal-revised}

Jennifer works in a medical school pathology lab as a research
assistant. The lab prepares human cadavers that are used to teach
medical students about anatomy. The cadavers come from people who had
donated their body for the general use of the researchers in the lab.
The bodies are normally cremated, however, severed cuts may be disposed
of at the discretion of lab researchers, One night Jennifer is leaving
the lab when she sees a body that is going to be discarded the next day.
Jennifer was a vegetarian, for moral reasons. She thought it was wrong
to kill animals for food. But then, when she saw a body about to be
cremated, she thought it was irrational to waste perfectly edible meat.
So she cut off a piece of flesh, and took it home and cooked it. The
person had died recently of a heart attack, and she cooked the meat
thoroughly, so there was no risk of disease

\subsection{Incest}\label{incest}

Julie and Mark, who are brother and sister, are travelling together in
France. They are both on summer vacation from college. One night they
are staying alone in a cabin near the beach. They decide that it would
be interesting and fun if they tried making love. At very least it would
be a new experience for each of them. Julie was already taking birth
control pills, but Mark uses a condom too, just to be safe. They both
enjoy it, but they decide not to do it again. They keep that night as a
special secret between them, which makes them feel even closer to each
other (Haidt et al., 2000).

\newpage

\section{Appendix B: Sample Statements to Challenge
Judgements}\label{appendix-b-sample-statements-to-challenge-judgements}

\subsection{Heinz/Druggist}\label{heinzdruggist}

\begin{itemize}
\tightlist
\item
  Do you agree that the druggist has to make a living?
\item
  And do you accept that Heinz broke into the druggist's store?
\item
  And do you accept that he stole from him?
\end{itemize}

~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~\_\_\_\_\_\_\_\_

\begin{itemize}
\tightlist
\item
  Do think that Heinz should try to save his wife's life?
\item
  And do you agree that he tried to get the money together
\item
  And do you accept that Heinz tried to negotiate with the druggist
\end{itemize}

\subsection{Trolley}\label{trolley-1}

\begin{itemize}
\tightlist
\item
  Do you accept that five people would have died if Paul didn't push the
  man?
\item
  And this man is the only way available to stop the trolley? (Paul does
  not weigh enough)
\item
  Do you agree that in stopping the trolley Paul saved the lives of five
  people?
\end{itemize}

\subsection{Cannibal}\label{cannibal}

\begin{itemize}
\tightlist
\item
  The body had been donated for research, it was to be discarded the
  next day. You must agree then that it had obviously fulfilled its
  purpose?
\item
  Do you accept that the body was already dead?
\item
  And do you accept that there was no risk of disease?
\end{itemize}

\subsection{Incest}\label{incest-1}

\begin{itemize}
\tightlist
\item
  Do you not agree that any concerns regarding reproductive
  complications are eased by their using of two forms of contraception?
\item
  And do you accept that they are both consenting adults, and that they
  both consented and enjoyed it?
\item
  And do you concede that nobody else was affected by their actions?
\end{itemize}

\newpage

\section{Appendix C: Post Discussion
Duestionnaire}\label{appendix-c-post-discussion-duestionnaire}

How sure were you about your judgement?

~~~~~~ 1 ~~~~~~ 2 ~~~~~~ 3 ~~~~~~ 4 ~~~~~~ 5 ~~~~~~ 6 ~~~~~~ 7

Not at all ~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~Extremely sure

~~~~~~~~~~~~~~~~~~~~~~~~~~~~~\_\_\_\_\_\_\_\_

How much did you change your mind?

~~~~~~ 1 ~~~~~~ 2 ~~~~~~ 3 ~~~~~~ 4 ~~~~~~ 5 ~~~~~~ 6 ~~~~~~ 7

Not at all ~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~Extremely

~~~~~~~~~~~~~~~~~~~~~~~~~~~~~\_\_\_\_\_\_\_\_

How confused were you?

~~~~~~ 1 ~~~~~~ 2 ~~~~~~ 3 ~~~~~~ 4 ~~~~~~ 5 ~~~~~~ 6 ~~~~~~ 7

Not at all ~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~Extremely
confused

~~~~~~~~~~~~~~~~~~~~~~~~~~~~~\_\_\_\_\_\_\_\_

How irritated were you?

~~~~~~ 1 ~~~~~~ 2 ~~~~~~ 3 ~~~~~~ 4 ~~~~~~ 5 ~~~~~~ 6 ~~~~~~ 7

Not at all ~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~Extremely
irritated

~~~~~~~~~~~~~~~~~~~~~~~~~~~~~\_\_\_\_\_\_\_\_

How much was your judgement based on reason?

~~~~~~ 1 ~~~~~~ 2 ~~~~~~ 3 ~~~~~~ 4 ~~~~~~ 5 ~~~~~~ 6 ~~~~~~ 7

Not at all ~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~Extremely

~~~~~~~~~~~~~~~~~~~~~~~~~~~~~\_\_\_\_\_\_\_\_

How much was your judgement based on ``gut'' feeling?

~~~~~~ 1 ~~~~~~ 2 ~~~~~~ 3 ~~~~~~ 4 ~~~~~~ 5 ~~~~~~ 6 ~~~~~~ 7

Not at all ~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~Extremely

\newpage

\subsection{Contributions:}\label{contributions}

\begin{itemize}
\tightlist
\item
  Substantial contributions to conception and design: CMH, MMG, ERI,
  ELK,
\item
  Acquisition of data: CMH
\item
  Analysis and interpretation of data: CMH, MMG, ERI, ELK,
\item
  Drafting the article or revising it critically for important
  intellectual content: CMH, MMG, ERI, ELK,
\item
  Final approval of the version to be published: CMH, MMG, ERI, ELK,
\end{itemize}

\subsection{Competing Interests:}\label{competing-interests}

The authors declare that there are no competing interests.

\subsection{Data accessibility
statement:}\label{data-accessibility-statement}

The following datasets were generated:

\begin{itemize}
\item
  SPSS data files (uploaded as supplemental material accompanying the
  submission)
\item
  R scripts outlining the analysis as described in the manuscript
  (uploaded as supplemental material accompanying the submission)
\end{itemize}
