---
title: "Study 6 Overview"
author: "Cillian McHugh"
date: "12th November 2021"
bibliography: "resources/bib/My Library.bib"
csl: "resources/bib/apa.csl"
output:
  bookdown::html_document2:
    fig_caption: yes
    toc: true
    toc_float:
      toc_collapsed: false
    toc_depth: 4
    number_sections: false
editor_options: 
  chunk_output_type: console
---

# Study 6

Below is an overview analysis for cognitive load Study 6.

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, include = FALSE)
# knitr::opts_chunk$set(eval = TRUE, echo = TRUE)
#knitr::opts_chunk$set(include = FALSE)
```



```{r load_libraries_cogload}
rm(list = ls())
library(citr)
#install.packages("sjstats")
library(plyr)
library(foreign)
library(car)
library(desnum)
library(ggplot2)
library(extrafont)
#devtools::install_github("crsh/papaja")
library(papaja)
#library("dplyr")
library("afex")
library("tibble")
library(scales)
#install.packages("metap")
library(metap)
library(pwr)
library(lsr)
#install.packages("sjstats")
library(sjstats)
library(DescTools)
#inatall.packages("ggstatsplot")
#library(ggstatsplot)
library(VGAM)
library(nnet)
library(mlogit)
library(reshape2)
#install.packages("powerMediation")
library("powerMediation")


#source("load_all_data.R")

#devtools::install_github("benmarwick/wordcountaddin")
#library(wordcountaddin)
#wordcountaddin::text_stats("cogload_1to5_25Sept19.Rmd")
getwd()
```



# Video Task

![Sample Video Task](resources/videos/num_scroll_test9.mp4)


```{r loaddatasetStudy6}
#source("~/Dropbox/College/research/Research_general/cog_load/moral_dumbfounding_and_cognitive_load/read_and_sort_raw_data.R")
#source("~/Dropbox/College/research/Research_general/cog_load/moral_dumbfounding_and_cognitive_load/load_study6_data.R")
rm(list = ls())

load("loaded_data/six.RData")
df3 <- study_6
#df3$InCS
df3 <- df3[which(is.na(df3$InCS)==FALSE),]
df3 <- df3[which(df3$InCS!="null"),]

df4 <- df3[which(df3$condition=="cog_load"),]
df5 <- df3[which(df3$condition=="control"),]
#df3$InCS <- df3$CS

```

# All Scenarios

## Sample size (with breakdown)

```{r checkingchanges6a, include=TRUE}

length(df3$gender)
table(df3$condition)
table(df3$country)
table(df3$condition,df3$scenario)


```

## Testing Effect of Cognitive Load

```{r checkingchanges6, include=TRUE}
chisq.test(table(df3$InCS,df3$condition),correct = TRUE)
```


```{r }

test <- as.data.frame.matrix((table(df3$InCS,df3$condition)))
`rownames<-`(test, c("nothing wrong","no reason","reasons"))
test <- as.matrix((test))
test1 <- cbind(test[,1],test[,2])
test2 <- `colnames<-`(test1, c("cognitive load","control"))

tb_count_perc <- function(x){
  tc <- table(x$InCS,x$condition)
  cbind(tc[,1],paste0(round(tc[,1]/sum(x$condition=="cog_load")*100),"%"),
        tc[,2],paste0(round(tc[,2]/sum(x$condition=="control")*100),"%"))
  }
  
  tb_count_perc_eng <- function(x){
  tc <- table(x$InCS,x$engaged)
  cbind(tc[,1],paste0(round(tc[,1]/sum(x$engaged=="engaged")*100),"%"),
        tc[,2],paste0(round(tc[,2]/sum(x$engaged=="not engaged")*100),"%"))
  }
  
  test <- tb_count_perc(df3)
  colnames(test) <- c("N","percent","N","percent")
  
  makespanners <- function(){
  cog_load <- c(2,3)
  control <- c(4,5)
  spans <- list(cog_load,control)
  names(spans) <- c("Cognitive Load","Control")
  spans
}

test <- tb_count_perc(df3)
#tb_count_perc(df3a)



```

## Frequency Table

```{r S6tab1dumb1all,results = 'asis', include=TRUE}


apa_table(
   test
   , align = c("l", "l", "c", "c", "c")
   , caption = "Study 6 – Response to the critical slide depending on cognitive load"
   #, added_stub_head = "Response to critical slide"
   , col_spanners = makespanners()
   #, note = "* = sig. at \\emph{p} < .05; ** = sig. at \\emph{p} < .001"
   , escape = FALSE
   
)

```


```{r}


y <- table(df3$condition,df3$InCS)
y <- as.data.frame(y)
colnames(y) <- c("condition","InCS","Freq")

z <- as.data.frame(table(df3$condition,df3$InCS)/length(df3$gender)*2)
perc <- z$Freq
test <- cbind(y,perc)
test$condition
test


#y <- table(df3$condition,df3$Dumb_incl_string)
#y <- as.data.frame(y)
#colnames(y) <- c("condition","InCS","Freq")

# z <- as.data.frame(table(df3$condition,df3$Dumb_incl_string)/length(df3$gender)*2)
# perc <- z$Freq
# test <- cbind(y,perc)
# test$condition
# test


ab_graph <- function(){
  a <- df3[which(df3$condition==levels(as.factor(df3$condition))[1]),]
  b <- df3[which(df3$condition==levels(as.factor(df3$condition))[2]),]
  a#levels(as.factor(df3$condition))[1]
  
  ay <- as.data.frame(table(a$InCS,as.character(a$condition)))
  by <- as.data.frame(table(b$InCS,as.character(b$condition)))
  
  aperc <- ay$Freq/length(a$gender)
  ay <- cbind(ay,aperc)
  colnames(ay) <- c("InCS","condition","Freq","perc")
  
  bperc <- by$Freq/length(b$gender)
  by <- cbind(by,bperc)
  colnames(by) <- c("InCS","condition","Freq","perc")
  
  c <- rbind(ay,by)
  
  c
}

test <- ab_graph()



rm(y)
```

## Plot

```{r}



g <- ggplot(test, aes(x=InCS, y=perc, fill=factor(condition,labels=c("Cognitive load","Control")))) +
  scale_y_continuous(limits = c(-.03,1),
                     labels = percent_format()
  )+ 
  geom_col(position = "dodge",
           color="black",
           size=.2
  )+
  geom_text(#family = "Times",
            size=4.2,
            aes( label = scales::percent(test$perc),
                 y= perc ),
            stat= "identity",
            vjust = -.5,
            position = position_dodge(.9),
            fontface='plain'
            )+
  geom_text(#family = "Times", 
            size=4.2,
            aes(label = format(Freq),
                y= -3*(..count../100)/(..count..)),
            stat= "count",
            position = position_dodge(0.9),
            #vjust = -.05,
            fontface='plain'
            ) +
  xlab("Response to Critical Slide") +
  ylab("Percentage of participants selecting each response")+
  scale_x_discrete(labels=c("Reasons", "Dumbfounded","Nothing Wrong")) +
  scale_fill_grey(start = .5, end = .8) +
  labs(fill="Condition") +
  
  geom_text(#family = "Times", 
            size=4.2,
            aes( label = scales::percent(test$perc),
                 y= test$perc ),
            stat= "identity",
            vjust = -.5,
            position = position_dodge(.9),
            fontface='plain'
            )+
  #theme_apa() +
  theme_bw() +
  theme(plot.title=element_text(#family="Times",
                                size=12
                                ),
        legend.text=element_text(#family="Times",
                                 size=8
                                 ),
          legend.title=element_text(#family="Times",
                                    size=10
                                    ),
          axis.text=element_text(#family="Times",
                                 colour = "black",
                                 size=8
                                 ),
          axis.ticks.x = element_blank(),
          axis.title=element_text(#family="Times",
                                  size=12
                                  ),
          strip.text=element_text(#family = "Times",
                                  size = 12
                                  ),
          strip.background = element_rect(fill = "white"),
          legend.position="right")





```

```{r ch5S6fig2criticalconditionb, fig.cap="Study 6: Responses to critical slide and for the experimental group and the control group", include=TRUE}
suppressWarnings(print(g))
```


```{r preptableS6}
c <- chisq.test(table(df3$InCS,df3$condition))
rownames(rbind(c$observed,c$expected,c$stdres))



ps <- function(y){
  if(as.numeric(sqrt( y*y) ) >3.3) print(paste0(y,"**"), quote = FALSE)
  else if(as.numeric(sqrt( y*y) ) >1.96) print(paste0(y,"*"), quote = FALSE)
  else print(y)}


x <- c$stdres
x <- round(x, digits = 2)

lapply(x, ps)

#c$stdres <- round(c$stdres,digits=3)
#c$stdres <- ps(c$stdres)

ps(x[1])
ps(x[2])
ps(x[3])

x <- `colnames<-`(
  cbind.data.frame(c(ps(x[1]),ps(x[2]),ps(x[3])),
                   c(ps(x[4]),ps(x[5]),ps(x[6]))),
  c("cog_load","control")
)

rownames(x) <- row.names(c$observed)  

y <- rbind(round(c$observed), round(c$expected, digits = 2))

c(c$stdres[1])


res <- cbind(c("Observed count","","","Expected count","","","Standardised residuals","",""),
      c("Reasons","Dumbfounded","Nothing Wrong",
        "Reasons","Dumbfounded","Nothing Wrong",
        "Reasons","Dumbfounded","Nothing Wrong"),
      rbind(y,x)
      
      )

row.names(res) <- NULL
colnames(res) <- c("","","Cognitive Load","Control")




```


## Residuals

```{r S6tab1dumb,results = 'asis', include=TRUE}


apa_table(
   res
   , align = c("l", "l", "c", "c", "c")
   , caption = "Study 6 – Observed counts, expected counts, and standardised residuals for each response to the critical slide depending on cognitive load"
   #, added_stub_head = "Response to critical slide"
   #, col_spanners = makespanners()
   , note = "* = sig. at \\emph{p} < .05; ** = sig. at \\emph{p} < .001"
   , escape = FALSE
   
)

```

# Each Scenario Individually

## Julie and Mark
### Sample size (with breakdown)
```{r}
df3 <- study_6
#df3$InCS
df3 <- df3[which(is.na(df3$InCS)==FALSE),]
df3 <- df3[which(df3$InCS!="null"),]

df3 <- df3[which(df3$scenario=="Incest"),]

df4 <- df3[which(df3$condition=="cog_load"),]
df5 <- df3[which(df3$condition=="control"),]

```

```{r checkingchanges6aIncest, include=TRUE}

length(df3$gender)
table(df3$condition)
#table(df3$condition,df3$scenario)

```

### Testing Effect of Cognitive Load

```{r checkingchanges6Incest, include=TRUE}
chisq.test(table(df3$InCS,df3$condition),correct = TRUE)
```


```{r }

test <- as.data.frame.matrix((table(df3$InCS,df3$condition)))
`rownames<-`(test, c("nothing wrong","no reason","reasons"))
test <- as.matrix((test))
test1 <- cbind(test[,1],test[,2])
test2 <- `colnames<-`(test1, c("cognitive load","control"))

tb_count_perc <- function(x){
  tc <- table(x$InCS,x$condition)
  cbind(tc[,1],paste0(round(tc[,1]/sum(x$condition=="cog_load")*100),"%"),
        tc[,2],paste0(round(tc[,2]/sum(x$condition=="control")*100),"%"))
  }
  
  tb_count_perc_eng <- function(x){
  tc <- table(x$InCS,x$engaged)
  cbind(tc[,1],paste0(round(tc[,1]/sum(x$engaged=="engaged")*100),"%"),
        tc[,2],paste0(round(tc[,2]/sum(x$engaged=="not engaged")*100),"%"))
  }
  
  test <- tb_count_perc(df3)
  colnames(test) <- c("N","percent","N","percent")
  
  makespanners <- function(){
  cog_load <- c(2,3)
  control <- c(4,5)
  spans <- list(cog_load,control)
  names(spans) <- c("Cognitive Load","Control")
  spans
}

test <- tb_count_perc(df3)
#tb_count_perc(df3a)



```

### Frequency Table

```{r S6tab1dumb1allIncest,results = 'asis', include=TRUE}


apa_table(
   test
   , align = c("l", "l", "c", "c", "c")
   , caption = "Study 6 – Response to the critical slide depending on cognitive load"
   #, added_stub_head = "Response to critical slide"
   , col_spanners = makespanners()
   #, note = "* = sig. at \\emph{p} < .05; ** = sig. at \\emph{p} < .001"
   , escape = FALSE
   
)

```


```{r}


y <- table(df3$condition,df3$InCS)
y <- as.data.frame(y)
colnames(y) <- c("condition","InCS","Freq")

z <- as.data.frame(table(df3$condition,df3$InCS)/length(df3$gender)*2)
perc <- z$Freq
test <- cbind(y,perc)
test$condition
test


#y <- table(df3$condition,df3$Dumb_incl_string)
#y <- as.data.frame(y)
#colnames(y) <- c("condition","InCS","Freq")

# z <- as.data.frame(table(df3$condition,df3$Dumb_incl_string)/length(df3$gender)*2)
# perc <- z$Freq
# test <- cbind(y,perc)
# test$condition
# test


ab_graph <- function(){
  a <- df3[which(df3$condition==levels(as.factor(df3$condition))[1]),]
  b <- df3[which(df3$condition==levels(as.factor(df3$condition))[2]),]
  a#levels(as.factor(df3$condition))[1]
  
  ay <- as.data.frame(table(a$InCS,as.character(a$condition)))
  by <- as.data.frame(table(b$InCS,as.character(b$condition)))
  
  aperc <- ay$Freq/length(a$gender)
  ay <- cbind(ay,aperc)
  colnames(ay) <- c("InCS","condition","Freq","perc")
  
  bperc <- by$Freq/length(b$gender)
  by <- cbind(by,bperc)
  colnames(by) <- c("InCS","condition","Freq","perc")
  
  c <- rbind(ay,by)
  
  c
}

test <- ab_graph()



rm(y)
```

### Plot

```{r}



g <- ggplot(test, aes(x=InCS, y=perc, fill=factor(condition,labels=c("Cognitive load","Control")))) +
  scale_y_continuous(limits = c(-.03,1),
                     labels = percent_format()
  )+ 
  geom_col(position = "dodge",
           color="black",
           size=.2
  )+
  geom_text(#family = "Times", 
            size=4.2,
            aes( label = scales::percent(test$perc),
                 y= perc ),
            stat= "identity",
            vjust = -.5,
            position = position_dodge(.9),
            fontface='plain'
            )+
  geom_text(#family = "Times", 
            size=4.2,
            aes(label = format(Freq),
                y= -3*(..count../100)/(..count..)),
            stat= "count",
            position = position_dodge(0.9),
            #vjust = -.05,
            fontface='plain'
            ) +
  xlab("Response to Critical Slide") +
  ylab("Percentage of participants selecting each response")+
  scale_x_discrete(labels=c("Reasons", "Dumbfounded","Nothing Wrong")) +
  scale_fill_grey(start = .5, end = .8) +
  labs(fill="Condition") +
  
  geom_text(#family = "Times",
            size=4.2,
            aes( label = scales::percent(test$perc),
                 y= test$perc ),
            stat= "identity",
            vjust = -.5,
            position = position_dodge(.9),
            fontface='plain'
            )+
  #theme_apa() +
  theme_bw() +
  theme(plot.title=element_text(#family="Times",
                                size=12
                                ),
        legend.text=element_text(#family="Times",
                                 size=8
                                 ),
          legend.title=element_text(#family="Times",
                                    size=10
                                    ),
          axis.text=element_text(#family="Times",
                                 colour = "black",
                                 size=8
                                 ),
          axis.ticks.x = element_blank(),
          axis.title=element_text(#family="Times",
                                  size=12
                                  ),
          strip.text=element_text(#family = "Times",
                                  size = 12
                                  ),
          strip.background = element_rect(fill = "white"),
          legend.position="right")





```

```{r ch5S6fig2criticalconditionbIncest, fig.cap="Study 6: Responses to critical slide and for the experimental group and the control group", include=TRUE}
suppressWarnings(print(g))
```


```{r}
c <- chisq.test(table(df3$InCS,df3$condition))
rownames(rbind(c$observed,c$expected,c$stdres))



ps <- function(y){
  if(as.numeric(sqrt( y*y) ) >3.3) print(paste0(y,"**"), quote = FALSE)
  else if(as.numeric(sqrt( y*y) ) >1.96) print(paste0(y,"*"), quote = FALSE)
  else print(y)}


x <- c$stdres
x <- round(x, digits = 2)

lapply(x, ps)

#c$stdres <- round(c$stdres,digits=3)
#c$stdres <- ps(c$stdres)

ps(x[1])
ps(x[2])
ps(x[3])

x <- `colnames<-`(
  cbind.data.frame(c(ps(x[1]),ps(x[2]),ps(x[3])),
                   c(ps(x[4]),ps(x[5]),ps(x[6]))),
  c("cog_load","control")
)

rownames(x) <- row.names(c$observed)  

y <- rbind(round(c$observed), round(c$expected, digits = 2))

c(c$stdres[1])


res <- cbind(c("Observed count","","","Expected count","","","Standardised residuals","",""),
      c("Reasons","Dumbfounded","Nothing Wrong",
        "Reasons","Dumbfounded","Nothing Wrong",
        "Reasons","Dumbfounded","Nothing Wrong"),
      rbind(y,x)
      
      )

row.names(res) <- NULL
colnames(res) <- c("","","Cognitive Load","Control")




```


### Residuals

```{r S6tab1dumbIncest,results = 'asis', include=TRUE}


apa_table(
   res
   , align = c("l", "l", "c", "c", "c")
   , caption = "Study 6 – Observed counts, expected counts, and standardised residuals for each response to the critical slide depending on cognitive load"
   #, added_stub_head = "Response to critical slide"
   #, col_spanners = makespanners()
   , note = "* = sig. at \\emph{p} < .05; ** = sig. at \\emph{p} < .001"
   , escape = FALSE
   
)

```


## Jennifer
### Sample size (with breakdown)
```{r}
df3 <- study_6
#df3$InCS
df3 <- df3[which(is.na(df3$InCS)==FALSE),]
df3 <- df3[which(df3$InCS!="null"),]

df3 <- df3[which(df3$scenario=="Jennifer"),]

df4 <- df3[which(df3$condition=="cog_load"),]
df5 <- df3[which(df3$condition=="control"),]

```

```{r checkingchanges6aJennifer, include=TRUE}

length(df3$gender)
table(df3$condition)
#table(df3$condition,df3$scenario)

```

### Testing Effect of Cognitive Load

```{r checkingchanges6Jennifer, include=TRUE}
chisq.test(table(df3$InCS,df3$condition),correct = TRUE)
```


```{r }

test <- as.data.frame.matrix((table(df3$InCS,df3$condition)))
`rownames<-`(test, c("nothing wrong","no reason","reasons"))
test <- as.matrix((test))
test1 <- cbind(test[,1],test[,2])
test2 <- `colnames<-`(test1, c("cognitive load","control"))

tb_count_perc <- function(x){
  tc <- table(x$InCS,x$condition)
  cbind(tc[,1],paste0(round(tc[,1]/sum(x$condition=="cog_load")*100),"%"),
        tc[,2],paste0(round(tc[,2]/sum(x$condition=="control")*100),"%"))
  }
  
  tb_count_perc_eng <- function(x){
  tc <- table(x$InCS,x$engaged)
  cbind(tc[,1],paste0(round(tc[,1]/sum(x$engaged=="engaged")*100),"%"),
        tc[,2],paste0(round(tc[,2]/sum(x$engaged=="not engaged")*100),"%"))
  }
  
  test <- tb_count_perc(df3)
  colnames(test) <- c("N","percent","N","percent")
  
  makespanners <- function(){
  cog_load <- c(2,3)
  control <- c(4,5)
  spans <- list(cog_load,control)
  names(spans) <- c("Cognitive Load","Control")
  spans
}

test <- tb_count_perc(df3)
#tb_count_perc(df3a)



```

### Frequency Table

```{r S6tab1dumb1allJennifer,results = 'asis', include=TRUE}


apa_table(
   test
   , align = c("l", "l", "c", "c", "c")
   , caption = "Study 6 – Response to the critical slide depending on cognitive load"
   #, added_stub_head = "Response to critical slide"
   , col_spanners = makespanners()
   #, note = "* = sig. at \\emph{p} < .05; ** = sig. at \\emph{p} < .001"
   , escape = FALSE
   
)

```


```{r}


y <- table(df3$condition,df3$InCS)
y <- as.data.frame(y)
colnames(y) <- c("condition","InCS","Freq")

z <- as.data.frame(table(df3$condition,df3$InCS)/length(df3$gender)*2)
perc <- z$Freq
test <- cbind(y,perc)
test$condition
test


#y <- table(df3$condition,df3$Dumb_incl_string)
#y <- as.data.frame(y)
#colnames(y) <- c("condition","InCS","Freq")

# z <- as.data.frame(table(df3$condition,df3$Dumb_incl_string)/length(df3$gender)*2)
# perc <- z$Freq
# test <- cbind(y,perc)
# test$condition
# test


ab_graph <- function(){
  a <- df3[which(df3$condition==levels(as.factor(df3$condition))[1]),]
  b <- df3[which(df3$condition==levels(as.factor(df3$condition))[2]),]
  a#levels(as.factor(df3$condition))[1]
  
  ay <- as.data.frame(table(a$InCS,as.character(a$condition)))
  by <- as.data.frame(table(b$InCS,as.character(b$condition)))
  
  aperc <- ay$Freq/length(a$gender)
  ay <- cbind(ay,aperc)
  colnames(ay) <- c("InCS","condition","Freq","perc")
  
  bperc <- by$Freq/length(b$gender)
  by <- cbind(by,bperc)
  colnames(by) <- c("InCS","condition","Freq","perc")
  
  c <- rbind(ay,by)
  
  c
}

test <- ab_graph()



rm(y)
```

### Plot

```{r}



g <- ggplot(test, aes(x=InCS, y=perc, fill=factor(condition,labels=c("Cognitive load","Control")))) +
  scale_y_continuous(limits = c(-.03,1),
                     labels = percent_format()
  )+ 
  geom_col(position = "dodge",
           color="black",
           size=.2
  )+
  geom_text(#family = "Times",
            size=4.2,
            aes( label = scales::percent(test$perc),
                 y= perc ),
            stat= "identity",
            vjust = -.5,
            position = position_dodge(.9),
            fontface='plain'
            )+
  geom_text(#family = "Times", 
            size=4.2,
            aes(label = format(Freq),
                y= -3*(..count../100)/(..count..)),
            stat= "count",
            position = position_dodge(0.9),
            #vjust = -.05,
            fontface='plain'
            ) +
  xlab("Response to Critical Slide") +
  ylab("Percentage of participants selecting each response")+
  scale_x_discrete(labels=c("Reasons", "Dumbfounded","Nothing Wrong")) +
  scale_fill_grey(start = .5, end = .8) +
  labs(fill="Condition") +
  
  geom_text(#family = "Times",
            size=4.2,
            aes( label = scales::percent(test$perc),
                 y= test$perc ),
            stat= "identity",
            vjust = -.5,
            position = position_dodge(.9),
            fontface='plain'
            )+
  #theme_apa() +
  theme_bw() +
  theme(plot.title=element_text(#family="Times",
                                size=12
                                ),
        legend.text=element_text(#family="Times",
                                 size=8
                                 ),
          legend.title=element_text(#family="Times",
                                    size=10
                                    ),
          axis.text=element_text(#family="Times",
                                 colour = "black",
                                 size=8
                                 ),
          axis.ticks.x = element_blank(),
          axis.title=element_text(#family="Times",
                                  size=12
                                  ),
          strip.text=element_text(#family = "Times",
                                  size = 12
                                  ),
          strip.background = element_rect(fill = "white"),
          legend.position="right")





```

```{r ch5S6fig2criticalconditionbJennifer, fig.cap="Study 6: Responses to critical slide and for the experimental group and the control group", include=TRUE}
suppressWarnings(print(g))
```


```{r}
c <- chisq.test(table(df3$InCS,df3$condition))
rownames(rbind(c$observed,c$expected,c$stdres))



ps <- function(y){
  if(as.numeric(sqrt( y*y) ) >3.3) print(paste0(y,"**"), quote = FALSE)
  else if(as.numeric(sqrt( y*y) ) >1.96) print(paste0(y,"*"), quote = FALSE)
  else print(y)}


x <- c$stdres
x <- round(x, digits = 2)

lapply(x, ps)

#c$stdres <- round(c$stdres,digits=3)
#c$stdres <- ps(c$stdres)

ps(x[1])
ps(x[2])
ps(x[3])

x <- `colnames<-`(
  cbind.data.frame(c(ps(x[1]),ps(x[2]),ps(x[3])),
                   c(ps(x[4]),ps(x[5]),ps(x[6]))),
  c("cog_load","control")
)

rownames(x) <- row.names(c$observed)  

y <- rbind(round(c$observed), round(c$expected, digits = 2))

c(c$stdres[1])


res <- cbind(c("Observed count","","","Expected count","","","Standardised residuals","",""),
      c("Reasons","Dumbfounded","Nothing Wrong",
        "Reasons","Dumbfounded","Nothing Wrong",
        "Reasons","Dumbfounded","Nothing Wrong"),
      rbind(y,x)
      
      )

row.names(res) <- NULL
colnames(res) <- c("","","Cognitive Load","Control")




```


### Residuals

```{r S6tab1dumbJennifer,results = 'asis', include=TRUE}


apa_table(
   res
   , align = c("l", "l", "c", "c", "c")
   , caption = "Study 6 – Observed counts, expected counts, and standardised residuals for each response to the critical slide depending on cognitive load"
   #, added_stub_head = "Response to critical slide"
   #, col_spanners = makespanners()
   , note = "* = sig. at \\emph{p} < .05; ** = sig. at \\emph{p} < .001"
   , escape = FALSE
   
)

```

## Trolley
### Sample size (with breakdown)
```{r}
df3 <- study_6
#df3$InCS
df3 <- df3[which(is.na(df3$InCS)==FALSE),]
df3 <- df3[which(df3$InCS!="null"),]

df3 <- df3[which(df3$scenario=="Trolley"),]

df4 <- df3[which(df3$condition=="cog_load"),]
df5 <- df3[which(df3$condition=="control"),]

```

```{r checkingchanges6aTrolley, include=TRUE}

length(df3$gender)
table(df3$condition)
#table(df3$condition,df3$scenario)

```

### Testing Effect of Cognitive Load

```{r checkingchanges6Trolley, include=TRUE}
chisq.test(table(df3$InCS,df3$condition),correct = TRUE)
```


```{r }

test <- as.data.frame.matrix((table(df3$InCS,df3$condition)))
`rownames<-`(test, c("nothing wrong","no reason","reasons"))
test <- as.matrix((test))
test1 <- cbind(test[,1],test[,2])
test2 <- `colnames<-`(test1, c("cognitive load","control"))

tb_count_perc <- function(x){
  tc <- table(x$InCS,x$condition)
  cbind(tc[,1],paste0(round(tc[,1]/sum(x$condition=="cog_load")*100),"%"),
        tc[,2],paste0(round(tc[,2]/sum(x$condition=="control")*100),"%"))
  }
  
  tb_count_perc_eng <- function(x){
  tc <- table(x$InCS,x$engaged)
  cbind(tc[,1],paste0(round(tc[,1]/sum(x$engaged=="engaged")*100),"%"),
        tc[,2],paste0(round(tc[,2]/sum(x$engaged=="not engaged")*100),"%"))
  }
  
  test <- tb_count_perc(df3)
  colnames(test) <- c("N","percent","N","percent")
  
  makespanners <- function(){
  cog_load <- c(2,3)
  control <- c(4,5)
  spans <- list(cog_load,control)
  names(spans) <- c("Cognitive Load","Control")
  spans
}

test <- tb_count_perc(df3)
#tb_count_perc(df3a)



```

### Frequency Table

```{r S6tab1dumb1allTrolley,results = 'asis', include=TRUE}


apa_table(
   test
   , align = c("l", "l", "c", "c", "c")
   , caption = "Study 6 – Response to the critical slide depending on cognitive load"
   #, added_stub_head = "Response to critical slide"
   , col_spanners = makespanners()
   #, note = "* = sig. at \\emph{p} < .05; ** = sig. at \\emph{p} < .001"
   , escape = FALSE
   
)

```


```{r}


y <- table(df3$condition,df3$InCS)
y <- as.data.frame(y)
colnames(y) <- c("condition","InCS","Freq")

z <- as.data.frame(table(df3$condition,df3$InCS)/length(df3$gender)*2)
perc <- z$Freq
test <- cbind(y,perc)
test$condition
test


#y <- table(df3$condition,df3$Dumb_incl_string)
#y <- as.data.frame(y)
#colnames(y) <- c("condition","InCS","Freq")

# z <- as.data.frame(table(df3$condition,df3$Dumb_incl_string)/length(df3$gender)*2)
# perc <- z$Freq
# test <- cbind(y,perc)
# test$condition
# test


ab_graph <- function(){
  a <- df3[which(df3$condition==levels(as.factor(df3$condition))[1]),]
  b <- df3[which(df3$condition==levels(as.factor(df3$condition))[2]),]
  a#levels(as.factor(df3$condition))[1]
  
  ay <- as.data.frame(table(a$InCS,as.character(a$condition)))
  by <- as.data.frame(table(b$InCS,as.character(b$condition)))
  
  aperc <- ay$Freq/length(a$gender)
  ay <- cbind(ay,aperc)
  colnames(ay) <- c("InCS","condition","Freq","perc")
  
  bperc <- by$Freq/length(b$gender)
  by <- cbind(by,bperc)
  colnames(by) <- c("InCS","condition","Freq","perc")
  
  c <- rbind(ay,by)
  
  c
}

test <- ab_graph()



rm(y)
```

### Plot

```{r}



g <- ggplot(test, aes(x=InCS, y=perc, fill=factor(condition,labels=c("Cognitive load","Control")))) +
  scale_y_continuous(limits = c(-.03,1),
                     labels = percent_format()
  )+ 
  geom_col(position = "dodge",
           color="black",
           size=.2
  )+
  geom_text(#family = "Times",
            size=4.2,
            aes( label = scales::percent(test$perc),
                 y= perc ),
            stat= "identity",
            vjust = -.5,
            position = position_dodge(.9),
            fontface='plain'
            )+
  geom_text(#family = "Times",
            size=4.2,
            aes(label = format(Freq),
                y= -3*(..count../100)/(..count..)),
            stat= "count",
            position = position_dodge(0.9),
            #vjust = -.05,
            fontface='plain'
            ) +
  xlab("Response to Critical Slide") +
  ylab("Percentage of participants selecting each response")+
  scale_x_discrete(labels=c("Reasons", "Dumbfounded","Nothing Wrong")) +
  scale_fill_grey(start = .5, end = .8) +
  labs(fill="Condition") +
  
  geom_text(#family = "Times",
            size=4.2,
            aes( label = scales::percent(test$perc),
                 y= test$perc ),
            stat= "identity",
            vjust = -.5,
            position = position_dodge(.9),
            fontface='plain'
            )+
  #theme_apa() +
  theme_bw() +
  theme(plot.title=element_text(#family="Times",
                                size=12
                                ),
        legend.text=element_text(#family="Times",
                                 size=8
                                 ),
          legend.title=element_text(#family="Times",
                                    size=10
                                    ),
          axis.text=element_text(#family="Times",
                                 colour = "black",
                                 size=8
                                 ),
          axis.ticks.x = element_blank(),
          axis.title=element_text(#family="Times",
                                  size=12
                                  ),
          strip.text=element_text(#family = "Times",
                                  size = 12
                                  ),
          strip.background = element_rect(fill = "white"),
          legend.position="right")





```

```{r ch5S6fig2criticalconditionbTrolley, fig.cap="Study 6: Responses to critical slide and for the experimental group and the control group", include=TRUE}
suppressWarnings(print(g))
```


```{r}
c <- chisq.test(table(df3$InCS,df3$condition))
rownames(rbind(c$observed,c$expected,c$stdres))



ps <- function(y){
  if(as.numeric(sqrt( y*y) ) >3.3) print(paste0(y,"**"), quote = FALSE)
  else if(as.numeric(sqrt( y*y) ) >1.96) print(paste0(y,"*"), quote = FALSE)
  else print(y)}


x <- c$stdres
x <- round(x, digits = 2)

lapply(x, ps)

#c$stdres <- round(c$stdres,digits=3)
#c$stdres <- ps(c$stdres)

ps(x[1])
ps(x[2])
ps(x[3])

x <- `colnames<-`(
  cbind.data.frame(c(ps(x[1]),ps(x[2]),ps(x[3])),
                   c(ps(x[4]),ps(x[5]),ps(x[6]))),
  c("cog_load","control")
)

rownames(x) <- row.names(c$observed)  

y <- rbind(round(c$observed), round(c$expected, digits = 2))

c(c$stdres[1])


res <- cbind(c("Observed count","","","Expected count","","","Standardised residuals","",""),
      c("Reasons","Dumbfounded","Nothing Wrong",
        "Reasons","Dumbfounded","Nothing Wrong",
        "Reasons","Dumbfounded","Nothing Wrong"),
      rbind(y,x)
      
      )

row.names(res) <- NULL
colnames(res) <- c("","","Cognitive Load","Control")




```


### Residuals

```{r S6tab1dumbTrolley,results = 'asis', include=TRUE}


apa_table(
   res
   , align = c("l", "l", "c", "c", "c")
   , caption = "Study 6 – Observed counts, expected counts, and standardised residuals for each response to the critical slide depending on cognitive load"
   #, added_stub_head = "Response to critical slide"
   #, col_spanners = makespanners()
   , note = "* = sig. at \\emph{p} < .05; ** = sig. at \\emph{p} < .001"
   , escape = FALSE
   
)

```

## Heinz
### Sample size (with breakdown)
```{r}
df3 <- study_6
#df3$InCS
df3 <- df3[which(is.na(df3$InCS)==FALSE),]
df3 <- df3[which(df3$InCS!="null"),]

df3 <- df3[which(df3$scenario=="Heinz"),]

df4 <- df3[which(df3$condition=="cog_load"),]
df5 <- df3[which(df3$condition=="control"),]

```

```{r checkingchanges6aHeinz, include=TRUE}

length(df3$gender)
table(df3$condition)
#table(df3$condition,df3$scenario)

```

### Testing Effect of Cognitive Load

```{r checkingchanges6Heinz, include=TRUE}
chisq.test(table(df3$InCS,df3$condition),correct = TRUE)
```


```{r }

test <- as.data.frame.matrix((table(df3$InCS,df3$condition)))
`rownames<-`(test, c("nothing wrong","no reason","reasons"))
test <- as.matrix((test))
test1 <- cbind(test[,1],test[,2])
test2 <- `colnames<-`(test1, c("cognitive load","control"))

tb_count_perc <- function(x){
  tc <- table(x$InCS,x$condition)
  cbind(tc[,1],paste0(round(tc[,1]/sum(x$condition=="cog_load")*100),"%"),
        tc[,2],paste0(round(tc[,2]/sum(x$condition=="control")*100),"%"))
  }
  
  tb_count_perc_eng <- function(x){
  tc <- table(x$InCS,x$engaged)
  cbind(tc[,1],paste0(round(tc[,1]/sum(x$engaged=="engaged")*100),"%"),
        tc[,2],paste0(round(tc[,2]/sum(x$engaged=="not engaged")*100),"%"))
  }
  
  test <- tb_count_perc(df3)
  colnames(test) <- c("N","percent","N","percent")
  
  makespanners <- function(){
  cog_load <- c(2,3)
  control <- c(4,5)
  spans <- list(cog_load,control)
  names(spans) <- c("Cognitive Load","Control")
  spans
}

test <- tb_count_perc(df3)
#tb_count_perc(df3a)



```

### Frequency Table

```{r S6tab1dumb1allHeinz,results = 'asis', include=TRUE}


apa_table(
   test
   , align = c("l", "l", "c", "c", "c")
   , caption = "Study 6 – Response to the critical slide depending on cognitive load"
   #, added_stub_head = "Response to critical slide"
   , col_spanners = makespanners()
   #, note = "* = sig. at \\emph{p} < .05; ** = sig. at \\emph{p} < .001"
   , escape = FALSE
   
)

```


```{r}


y <- table(df3$condition,df3$InCS)
y <- as.data.frame(y)
colnames(y) <- c("condition","InCS","Freq")

z <- as.data.frame(table(df3$condition,df3$InCS)/length(df3$gender)*2)
perc <- z$Freq
test <- cbind(y,perc)
test$condition
test


#y <- table(df3$condition,df3$Dumb_incl_string)
#y <- as.data.frame(y)
#colnames(y) <- c("condition","InCS","Freq")

# z <- as.data.frame(table(df3$condition,df3$Dumb_incl_string)/length(df3$gender)*2)
# perc <- z$Freq
# test <- cbind(y,perc)
# test$condition
# test


ab_graph <- function(){
  a <- df3[which(df3$condition==levels(as.factor(df3$condition))[1]),]
  b <- df3[which(df3$condition==levels(as.factor(df3$condition))[2]),]
  a#levels(as.factor(df3$condition))[1]
  
  ay <- as.data.frame(table(a$InCS,as.character(a$condition)))
  by <- as.data.frame(table(b$InCS,as.character(b$condition)))
  
  aperc <- ay$Freq/length(a$gender)
  ay <- cbind(ay,aperc)
  colnames(ay) <- c("InCS","condition","Freq","perc")
  
  bperc <- by$Freq/length(b$gender)
  by <- cbind(by,bperc)
  colnames(by) <- c("InCS","condition","Freq","perc")
  
  c <- rbind(ay,by)
  
  c
}

test <- ab_graph()



rm(y)
```

### Plot

```{r}



g <- ggplot(test, aes(x=InCS, y=perc, fill=factor(condition,labels=c("Cognitive load","Control")))) +
  scale_y_continuous(limits = c(-.03,1),
                     labels = percent_format()
  )+ 
  geom_col(position = "dodge",
           color="black",
           size=.2
  )+
  geom_text(#family = "Times",
            size=4.2,
            aes( label = scales::percent(test$perc),
                 y= perc ),
            stat= "identity",
            vjust = -.5,
            position = position_dodge(.9),
            fontface='plain'
            )+
  geom_text(#family = "Times",
            size=4.2,
            aes(label = format(Freq),
                y= -3*(..count../100)/(..count..)),
            stat= "count",
            position = position_dodge(0.9),
            #vjust = -.05,
            fontface='plain'
            ) +
  xlab("Response to Critical Slide") +
  ylab("Percentage of participants selecting each response")+
  scale_x_discrete(labels=c("Reasons", "Dumbfounded","Nothing Wrong")) +
  scale_fill_grey(start = .5, end = .8) +
  labs(fill="Condition") +
  
  geom_text(#family = "Times",
            size=4.2,
            aes( label = scales::percent(test$perc),
                 y= test$perc ),
            stat= "identity",
            vjust = -.5,
            position = position_dodge(.9),
            fontface='plain'
            )+
  #theme_apa() +
  theme_bw() +
  theme(plot.title=element_text(#family="Times",
                                size=12
                                ),
        legend.text=element_text(#family="Times",
                                 size=8
                                 ),
          legend.title=element_text(#family="Times",
                                    size=10
                                    ),
          axis.text=element_text(#family="Times",
                                 colour = "black",
                                 size=8
                                 ),
          axis.ticks.x = element_blank(),
          axis.title=element_text(#family="Times",
                                  size=12
                                  ),
          strip.text=element_text(#family = "Times",
                                  size = 12
                                  ),
          strip.background = element_rect(fill = "white"),
          legend.position="right")





```

```{r ch5S6fig2criticalconditionbHeinz, fig.cap="Study 6: Responses to critical slide and for the experimental group and the control group", include=TRUE}
suppressWarnings(print(g))
```


```{r}
c <- chisq.test(table(df3$InCS,df3$condition))
rownames(rbind(c$observed,c$expected,c$stdres))



ps <- function(y){
  if(as.numeric(sqrt( y*y) ) >3.3) print(paste0(y,"**"), quote = FALSE)
  else if(as.numeric(sqrt( y*y) ) >1.96) print(paste0(y,"*"), quote = FALSE)
  else print(y)}


x <- c$stdres
x <- round(x, digits = 2)

lapply(x, ps)

#c$stdres <- round(c$stdres,digits=3)
#c$stdres <- ps(c$stdres)

ps(x[1])
ps(x[2])
ps(x[3])

x <- `colnames<-`(
  cbind.data.frame(c(ps(x[1]),ps(x[2]),ps(x[3])),
                   c(ps(x[4]),ps(x[5]),ps(x[6]))),
  c("cog_load","control")
)

rownames(x) <- row.names(c$observed)  

y <- rbind(round(c$observed), round(c$expected, digits = 2))

c(c$stdres[1])


res <- cbind(c("Observed count","","","Expected count","","","Standardised residuals","",""),
      c("Reasons","Dumbfounded","Nothing Wrong",
        "Reasons","Dumbfounded","Nothing Wrong",
        "Reasons","Dumbfounded","Nothing Wrong"),
      rbind(y,x)
      
      )

row.names(res) <- NULL
colnames(res) <- c("","","Cognitive Load","Control")




```


### Residuals

```{r S6tab1dumbHeinz,results = 'asis', include=TRUE}


apa_table(
   res
   , align = c("l", "l", "c", "c", "c")
   , caption = "Study 6 – Observed counts, expected counts, and standardised residuals for each response to the critical slide depending on cognitive load"
   #, added_stub_head = "Response to critical slide"
   #, col_spanners = makespanners()
   , note = "* = sig. at \\emph{p} < .05; ** = sig. at \\emph{p} < .001"
   , escape = FALSE
   
)

```