---
title: "US Sample Analysis"
author: "Cillian McHugh"
date: "1st November 2021"
bibliography: "resources/bib/My Library.bib"
csl: "resources/bib/apa.csl"
output:
  bookdown::html_document2:
    fig_caption: yes
    toc: true
    toc_float:
      toc_collapsed: false
    toc_depth: 4
    number_sections: false
editor_options: 
  chunk_output_type: console
---

# Sample Analysis

Below is a sample analysis for cognitive load Study 6.

```{r setup, include=FALSE}
#knitr::opts_chunk$set(echo = FALSE)
knitr::opts_chunk$set(eval = TRUE, echo = TRUE)
#knitr::opts_chunk$set(include = FALSE)
```



```{r load_libraries_cogload}
rm(list = ls())
library(citr)
#install.packages("sjstats")
library(plyr)
library(foreign)
library(car)
library(desnum)
library(ggplot2)
library(extrafont)
#devtools::install_github("crsh/papaja")
library(papaja)
#library("dplyr")
library("afex")
library("tibble")
library(scales)
#install.packages("metap")
library(metap)
library(pwr)
library(lsr)
#install.packages("sjstats")
library(sjstats)
library(DescTools)
#inatall.packages("ggstatsplot")
#library(ggstatsplot)
library(VGAM)
library(nnet)
library(mlogit)
library(reshape2)
#install.packages("powerMediation")
library("powerMediation")


#source("load_all_data.R")

#devtools::install_github("benmarwick/wordcountaddin")
#library(wordcountaddin)
#wordcountaddin::text_stats("cogload_1to5_25Sept19.Rmd")
getwd()
```



# Study 6: Video Task

![Hypothesised relationship between responses in the dumbfounding paradigm and level of deliberation](resources/videos/num_scroll_test9.mp4)


```{r load data set Study 6}
source("~/Dropbox/College/research/Research_general/cog_load/moral_dumbfounding_and_cognitive_load/read_and_sort_raw_data_US.R")
source("~/Dropbox/College/research/Research_general/cog_load/moral_dumbfounding_and_cognitive_load/load_all_data_US.R")
rm(list = ls())

load("loaded_data/six.RData")
df3 <- study_6
#df3$InCS
df3 <- df3[which(is.na(df3$InCS)==FALSE),]
df3 <- df3[which(df3$InCS!="null"),]

df4 <- df3[which(df3$condition=="cog_load"),]
df5 <- df3[which(df3$condition=="control"),]
#df3$InCS <- df3$CS

```

# Tests

```{r checkingchanges6, echo=FALSE, include=TRUE}

length(df3$gender)

# t_j1 <- t.test(df3$InJu1 ~ df3$condition)
# d_j1 <- cohensD(df3$InJu1 ~ df3$condition)

#t_j1 <- t.test(college$InJu1 ~ college$condition)
#t_paragraph(college$InJu1, college$condition, "initial judgement")
#t_paragraph(one$InJu1, one$condition, "initial judgement")
#t_paragraph(two$InJu1, two$condition, "initial judgement")
#t_paragraph(three$InJu1, three$condition, "initial judgement")
table(df3$condition)
table(df3$condition,df3$scenario)

chisq.test(table(df3$InCS,df3$condition),correct = FALSE)
chisq.test(table(df3$InCS,df3$condition),correct = TRUE)

#
```





```{r playwithstudy6}
#table(df3a$InCS,df3a$condition)
#chisq.test(table(df3$InCS,df3$condition))

#table(df3$reason,df3$condition)
#chisq.test(table(df3$reason,df3$condition))



# table(df3$InCS, df3$cog_number_right)
# df4a <- df4[which(df4$cog_number_right>2),]
# df3a <- rbind(df4a,df5)

table(df3$InCS,df3$condition)
chisq.test(table(df3$InCS,df3$condition))




## what's going on???

#df3[which(df3$InCS!="It's wrong and I can provide a valid reason."&df3$condition=="cog_load"),]



# df7 <- rbind(df7,
#              df3[which(df3$participant=="3"),],
#              df3[which(df3$participant=="6"),],
#              df3[which(df3$participant=="12"),],
#              df3[which(df3$participant=="14"),])
# 
# df7 <- rbind(df7,
#              df3[which(df3$participant=="14"),])

# table(df7$InCS,df7$condition)
# chisq.test(table(df7$InCS,df7$condition))
# 
# df8 <- rbind(df3,df3)
# table(df8$InCS,df8$condition)
# chisq.test(table(df8$InCS,df8$condition))

table(df3$InCS,df3$condition)

test <- as.data.frame.matrix((table(df3$InCS,df3$condition)))
`rownames<-`(test, c("nothing wrong","no reason","reasons"))
test <- as.matrix((test))
test1 <- cbind(test[,1],test[,2])
test2 <- `colnames<-`(test1, c("cognitive load","control"))

tb_count_perc <- function(x){
  tc <- table(x$InCS,x$condition)
  cbind(tc[,1],paste0(round(tc[,1]/sum(x$condition=="cog_load")*100),"%"),
        tc[,2],paste0(round(tc[,2]/sum(x$condition=="control")*100),"%"))
  }
  
  tb_count_perc_eng <- function(x){
  tc <- table(x$InCS,x$engaged)
  cbind(tc[,1],paste0(round(tc[,1]/sum(x$engaged=="engaged")*100),"%"),
        tc[,2],paste0(round(tc[,2]/sum(x$engaged=="not engaged")*100),"%"))
  }
  
  test <- tb_count_perc(df3)
  colnames(test) <- c("N","percent","N","percent")
  
  makespanners <- function(){
  cog_load <- c(2,3)
  control <- c(4,5)
  spans <- list(cog_load,control)
  names(spans) <- c("Cognitive Load","Control")
  spans
}

test <- tb_count_perc(df3)
#tb_count_perc(df3a)



```



```{r S6tab1dumb1,results = 'asis', include=TRUE}


apa_table(
   test
   , align = c("l", "l", "c", "c", "c")
   , caption = "Study 6 – Response to the critical slide depending on cognitive load"
   #, added_stub_head = "Response to critical slide"
   #, col_spanners = makespanners()
   #, note = "* = sig. at \\emph{p} < .05; ** = sig. at \\emph{p} < .001"
   , escape = FALSE
   
)

```


```{r prepch6S6fig2}


y <- table(df3$condition,df3$InCS)
y <- as.data.frame(y)
colnames(y) <- c("condition","InCS","Freq")

z <- as.data.frame(table(df3$condition,df3$InCS)/length(df3$gender)*2)
perc <- z$Freq
test <- cbind(y,perc)
test$condition
test


#y <- table(df3$condition,df3$Dumb_incl_string)
#y <- as.data.frame(y)
#colnames(y) <- c("condition","InCS","Freq")

# z <- as.data.frame(table(df3$condition,df3$Dumb_incl_string)/length(df3$gender)*2)
# perc <- z$Freq
# test <- cbind(y,perc)
# test$condition
# test


ab_graph <- function(){
  a <- df3[which(df3$condition==levels(as.factor(df3$condition))[1]),]
  b <- df3[which(df3$condition==levels(as.factor(df3$condition))[2]),]
  a#levels(as.factor(df3$condition))[1]
  
  ay <- as.data.frame(table(a$InCS,as.character(a$condition)))
  by <- as.data.frame(table(b$InCS,as.character(b$condition)))
  
  aperc <- ay$Freq/length(a$gender)
  ay <- cbind(ay,aperc)
  colnames(ay) <- c("InCS","condition","Freq","perc")
  
  bperc <- by$Freq/length(b$gender)
  by <- cbind(by,bperc)
  colnames(by) <- c("InCS","condition","Freq","perc")
  
  c <- rbind(ay,by)
  
  c
}

test <- ab_graph()



rm(y)
```

# Plot

```{r ch5S6fig2criticalcondition, fig.cap="Study 6: Responses to critical slide and for the experimental group (*N* = 98) and the control group (*N* = 106)", include=TRUE}



ggplot(test, aes(x=InCS, y=perc, fill=factor(condition,labels=c("Cognitive load","Control")))) +
  scale_y_continuous(limits = c(-.03,1),
                     labels = percent_format()
  )+ 
  geom_col(position = "dodge",
           color="black",
           size=.2
  )+
  geom_text(family = "Times", size=4.2,
            aes( label = scales::percent(test$perc),
                 y= perc ),
            stat= "identity",
            vjust = -.5,
            position = position_dodge(.9),
            fontface='plain'
            )+
  geom_text(family = "Times", size=4.2,
            aes(label = format(Freq),
                y= -3*(..count../100)/(..count..)),
            stat= "count",
            position = position_dodge(0.9),
            #vjust = -.05,
            fontface='plain'
            ) +
  xlab("Response to Critical Slide") +
  ylab("Percentage of participants selecting each response")+
  #scale_x_discrete(labels=c("Nothing Wrong", "Dumbfounded","Reasons")) +
  scale_fill_grey(start = .5, end = .8) +
  labs(fill="Condition") +
  
  geom_text(family = "Times", size=4.2,
            aes( label = scales::percent(test$perc),
                 y= test$perc ),
            stat= "identity",
            vjust = -.5,
            position = position_dodge(.9),
            fontface='plain'
            )+
  #theme_apa() +
  theme_bw() +
  theme(plot.title=element_text(family="Times",
                                size=12
                                ),
        legend.text=element_text(family="Times",
                                 size=8
                                 ),
          legend.title=element_text(family="Times",
                                    size=10
                                    ),
          axis.text=element_text(family="Times",
                                 colour = "black",
                                 size=8
                                 ),
          axis.ticks.x = element_blank(),
          axis.title=element_text(family="Times",
                                  size=12
                                  ),
          strip.text=element_text(family = "Times",
                                  size = 12
                                  ),
          strip.background = element_rect(fill = "white"),
          legend.position="right")





```


```{r preptableS6}
c <- chisq.test(table(df3$InCS,df3$condition))
rownames(rbind(c$observed,c$expected,c$stdres))



ps <- function(y){
  if(as.numeric(sqrt( y*y) ) >3.3) print(paste0(y,"**"), quote = FALSE)
  else if(as.numeric(sqrt( y*y) ) >1.96) print(paste0(y,"*"), quote = FALSE)
  else print(y)}


x <- c$stdres
x <- round(x, digits = 2)

lapply(x, ps)

#c$stdres <- round(c$stdres,digits=3)
#c$stdres <- ps(c$stdres)

ps(x[1])
ps(x[2])
ps(x[3])

x <- `colnames<-`(
  cbind.data.frame(c(ps(x[1]),ps(x[2]),ps(x[3])),
                   c(ps(x[4]),ps(x[5]),ps(x[6]))),
  c("cog_load","control")
)

rownames(x) <- row.names(c$observed)  

y <- rbind(round(c$observed), round(c$expected, digits = 2))

c(c$stdres[1])


res <- cbind(c("Observed count","","","Expected count","","","Standardised residuals","",""),
      c("Nothing Wrong","Dumbfounded","Reasons",
        "Nothing Wrong","Dumbfounded","Reasons",
        "Nothing Wrong","Dumbfounded","Reasons"),
      rbind(y,x)
      
      )

row.names(res) <- NULL
colnames(res) <- c("","","Cognitive Load","Control")




```




```{r S6tab1dumb,results = 'asis', include=TRUE}


apa_table(
   res
   , align = c("l", "l", "c", "c", "c")
   , caption = "Study 6 – Observed counts, expected counts, and standardised residuals for each response to the critical slide depending on cognitive load"
   #, added_stub_head = "Response to critical slide"
   #, col_spanners = makespanners()
   , note = "* = sig. at \\emph{p} < .05; ** = sig. at \\emph{p} < .001"
   , escape = FALSE
   
)

```

# Data Accessibility Statement
All participant data, and analysis scripts can be found on this paper’s project page on the Open Science Framework at [https://osf.io/wge5t/](https://osf.io/wge5t/).

```{r reasonsR_citations, include=FALSE}

r_refs(file = "r-references.bib")
my_citation <- cite_r(file = "r-references.bib")
my_citation
```

All statistical analysis was conducted using `r my_citation`.



# References

```{r create_r-references}
r_refs(file = "r-references.bib")
```

