---
title             : "Cognitive Load Reduces Reason-Giving in a Moral Dumbfounding Task"
shorttitle        : "Cognitive Load and Moral Dumbfounding"
author:
  - name          : "Cillian McHugh"
    affiliation   : "1"
    corresponding : yes    # Define only one corresponding author
    address       : "Department of Psychology, University of Limerick"
    email         : "cillian.mchugh@ul.ie"
  - name          : "Marek McGann"
    affiliation   : "2"
  - name          : "Eric R. Igou"
    affiliation   : "1"
  - name          : "Elaine L. Kinsella"
    affiliation   : "1"
affiliation:
  - id            : "1"
    institution   : "Department of Psychology, University of Limerick"
  - id            : "2"
    institution   : "Department of Psychology, Mary Immaculate College, University of Limerick"
author_note: >
  All procedures performed in studies involving human participants were approved by institutional research ethics committee and conducted in accordance with the Code of Professional Ethics of the Psychological Society of Ireland, and with the 1964 Helsinki declaration and its later amendments or comparable ethical standards. Informed consent was obtained from all individual participants included in the study. The authors declare that there are no potential conflicts of interest with respect to the research, authorship, and/or publication of this article. All authors consented to the submission of this manuscript. 
abstract: >
  Moral dumbfounding occurs when people defend a moral judgment, without reasons in support of this judgment. The phenomenon has been influential in moral psychology, however, despite its influence, it remains poorly understood. Based on the notion that cognitive load enhances biases and shortcomings in human judgment when elaboration is beneficial, we hypothesized that under cognitive load, people would be less likely to provide reasons for a judgment and more likely to be dumbfounded. In a pre-registered study (N = 1686) we tested this prediction. Our findings suggest that cognitive load reduces reason-giving, leading to increases in dumbfounding. Our results provide new insights into the phenomenon of moral dumbfounding while also advancing theory in moral psychology.   
keywords          : "moral dumbfounding, morality, cognitive load, dual-processes"
wordcount         : "5,201"
bibliography: "../resources/bib/My Library.bib"
floatsintext      : yes
linenumbers       : yes
draft             : no
mask              : no
figurelist        : no
tablelist         : no
footnotelist      : no
classoption       : "man"
output:
  papaja::apa6_pdf:
       keep_tex: true
header-includes:
- \raggedbottom
editor_options: 
  chunk_output_type: console
---



```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, include = FALSE)
# knitr::opts_chunk$set(eval = TRUE, echo = TRUE)
#knitr::opts_chunk$set(include = FALSE)
```


```{r load_libraries_cogload}
rm(list = ls())
library(citr)
#install.packages("sjstats")
library(plyr)
library(foreign)
library(car)
library(desnum)
library(ggplot2)
library(extrafont)
#devtools::install_github("crsh/papaja")
library(papaja)
#library("dplyr")
library("afex")
library("tibble")
library(scales)
#install.packages("metap")
library(metap)
library(pwr)
library(lsr)
#install.packages("sjstats")
library(sjstats)
library(DescTools)
#inatall.packages("ggstatsplot")
#library(ggstatsplot)
library(VGAM)
library(nnet)
library(mlogit)
library(reshape2)
#install.packages("powerMediation")
library("powerMediation")


#source("load_all_data.R")


#devtools::install_github("benmarwick/wordcountaddin")
#library(wordcountaddin)
#wordcountaddin::text_stats("cogload_1to5_25Sept19.Rmd")
getwd()


#papaja::render_appendix("appendix.Rmd")

```



```{r child = 'Introduction.Rmd'}
```


```{r child = 'Main_Study.Rmd'}
```


\newpage

```{r child = 'Discussion.Rmd'}
```

\newpage


\setlength{\parindent}{0.0in}
\setlength{\leftskip}{0.0in}
\setlength{\parskip}{8pt}


# Contributions

Contributed to Conception and design: CMH, MMG, ERI, ELK

Contributed to acquisition of data: CMH

Contributed to analysis and interpretation of data: CMH, MMG, ERI, ELK

Drafted and/or revised the article: CMH, MMG, ERI, ELK

Approved the submitted version for publication: CMH, MMG, ERI, ELK

# Funding Information

The Study reported here was funded by University of Limerick, Education and Health Sciences seed funding. Study S5 was funded by Mary Immaculate College seed funding. 

# Data Accessibility Statement
All data and analysis code are publicly available on this project's OSF page at [https://osf.io/fcd5r/?view_only=9fb6e506e53340c189b98453bb2b6eaf](https://osf.io/fcd5r/?view_only=9fb6e506e53340c189b98453bb2b6eaf). Materials are also available including the full text of the jsPsych script.

# Figure Titles

## Main Manuscript

Figure 1: Hypothesized relationship between deliberation and responses in the dumbfounding paradigm

Figure 2: Responses to critical slide depending on cognitive load

Figure 3: Responses to critical slide and for the experimental group and the control group for each scenario

## Supplementary Materials

Figure 1: Screenshot of Attention Check

Figure 2: Screenshot of Attention Check

Figure 3: Study S1: Responses to critical slide and for the experimental group (*N* = 33) and the control group (*N* = 33)

Figure 4: Study S1: Probability of selecting each response to the critical slide depending on Need for Cognition

Figure 5: Sample dot patterns - more simple for the control group (a) and higher complexity for the experimental condition (b)

Figure 6: Study S2: Responses to critical slide for (left) the experimental group (*N* = 51) vs the control group (*N* = 49); and (right) depending on engagement (*N* = 56) or non-engagement (*N* = 44) with the memory task

Figure 7: Study S2: Probability of selecting each response to the critical slide depending on Need for Cognition

Figure 8: Study S3: Responses to critical slide for the cognitive load group (*N* = 68) and the control group (*N* = 61)

Figure 9: Study S3: Probability of selecting each response to the critical slide depending on Need for Cognition

Figure 10: Study S4: Responses to critical slide for the cognitive load group (*N* = 64) and the control group (*N* = 61)

Figure 11: Study S4: Probability of selecting each response to the critical slide depending on Need for Cognition

Figure 12: Study S5: Responses to critical slide and for the experimental group (*N* = 98) and the control group (*N* = 106)

Figure 13: Study S5: Probability of selecting each response to the critical slide depending on Need for Cognition







# References

\setlength{\parindent}{-0.5in}
\setlength{\leftskip}{0.5in}
\setlength{\parskip}{8pt}


