---
title             : "Understanding Moral Dumbfounding: Cognitive Load Increases the Liklihood of Moral Dumbfounding"
shorttitle        : "Cognitive Load and Moral Dumbfounding"

author:
  - name          : "Cillian McHugh"
    affiliation   : "1"
    corresponding : yes    # Define only one corresponding author
    address       : "University of Limerick, Limerick, Ireland, V94 T9PX"
    email         : "cillian.mchugh@ul.ie"
  - name          : "Marek McGann"
    affiliation   : "2"
  - name          : "Eric R. Igou"
    affiliation   : "1"
  - name          : "Elaine L Kinsella"
    affiliation   : "1"


affiliation:
  - id            : "1"
    institution   : "University of Limerick"
  - id            : "2"
    institution   : "Mary Immaculate College ~ University of Limerick"

author_note: >
  All procedures performed in studies involving human participants were approved by institutional research ethics committee and conducted in accordance with the Code of Professional Ethics of the Psychological Society of Ireland, and with the 1964 Helsinki declaration and its later amendments or comparable ethical standards. Informed consent was obtained from all individual participants included in the study. The authors declare that there are no potential conflicts of interest with respect to the research, authorship, and/or publication of this article. All authors consented to the submission of this manuscript.

abstract: >
  Six studies etc.
keywords          : "keywords"
wordcount         : "TBC"

bibliography: "../resources/bib/My Library.bib"
csl: "../resources/bib/apa6.csl"

figsintext        : yes
figurelist        : no
tablelist         : no
footnotelist      : no
lineno            : no
toc               : no

lang              : "en-US"
documentclass     : "apa7"
output:
  papaja::apa6_pdf

---

```{r Discussionsetup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, include = FALSE)
# knitr::opts_chunk$set(eval = TRUE, echo = TRUE)
#knitr::opts_chunk$set(include = FALSE)
```


```{r}
library("papaja")
#library("wordcountaddin")
#wordcountaddin::word_count("Introduction.Rmd")
getwd()
#devtools::install_github("benmarwick/wordcountaddin", type = "source", dependencies = TRUE)
```
# Discussion

The present research aimed to add to the literature on moral judgments by offering new insights into factors that prompt moral dumbfounding. We hypothesized that under cognitive load, participants would be less likely to provide reasons and more likely to present as dumbfounded (or to select nothing wrong). When participants engaged in a secondary task while completing a dumbfounding task reason-giving was inhibited for three out of four scenarios tested. Overall we find evidence that in situations where the resources available for deliberation are limited (as when cognitive load is high), reason-giving is reduced, and moral dumbfounding is more likely. This key finding is consistent with previous work demonstrating that cognitive load inhibits deliberative responding [@deneys_dual_2006; @evans_rapid_2005].

## Implications, Limitations, and Future Directions

These studies offer new understandings of the phenomenon of moral dumbfounding. While our studies illustrate the complexity of attempting to understand moral judgments, we do demonstrate some reliable patterns that offer support to our core theoretically-informed hypotheses. Furthermore, these studies showcase a methodology for measuring dumbfounding under different empirical conditions, offering a path for future researchers to explore the role of other contextual and individual difference variables in influencing moral dumbfounding.

From a theoretical perspective, our findings are consistent with a dual-process explanation of moral dumbfounding, whereby dumbfounding occurs when an intuitive/habitual response is in conflict with a deliberative response [@evans_resolution_2007; again we note that the assumption of dual-processes is not necessarily required, and that this prediction is also consistent with the unimodel, @kruglanski_intuitive_2011; or categorization approaches @mchugh_moral_2022]. In line with existing theorizing on moral judgments [@cushman_action_2013; @mchugh_moral_2022; @railton_moral_2017], we propose that an individual may make an intuitive judgment and that subsequent attempts to identify reasons for this judgment occur through deliberation. If deliberation is unsuccessful and the individual does not revise their judgment, dumbfounding is observed. In support of this explanation, our studies demonstrated that by reducing the cognitive resources available for deliberation, reason-giving was reduced and dumbfounding increased.

Our results do display some unexplained variability, with the *classic* dumbfounding scenario (*Julie and Mark*) showing no significant change in responding with increased cognitive load (we note that the pilot studies used only this scenario and also showed mixed results). An exploratory follow-up test for equivalence did not provide evidence for the absence of an effect; thus, our results regarding *Julie and Mark* are inconclusive.

One potential explanation for this may point to an overall tendency for participants to be less likely to provide reasons for their judgment of *Julie and Mark* than for the other scenarios. This would be in line with its apparent standing as the *classic* dumbfounding scenario [@haidt_emotional_2001; @royzman_curious_2015]. Examination of Figure 3 seems to provide some support for this interpretation. In the control condition, the rate of providing reasons was lowest for *Julie and Mark*, and this remained descriptively lower than rates of reason-giving for both *Heinz* and *Jennifer* in the cognitive load conditions (i.e., rates of reason-giving for both *Heinz* and *Jennifer* were higher under cognitive load than rates of reason-giving in the control condition for *Julie and Mark*). It is possible that any effect of cognitive load on reason-giving was confounded by this lower base rate of reason-giving. We note however that this interpretation is not necessarily supported when the results for *Julie and Mark* are compared with the results for *Trolley*. That is, rates of reason-giving for Trolley under cognitive load were lower than rates of reason-giving for *Julie and Mark* in either condition. Future research should attempt to better understand these findings.

It is also possible that these inconclusive results reflect a lack of statistical power. Recall that a sample of *N* = 1966 was required to detect a small effect size (*V* = .07) with 80% power. It is possible that cognitive load does reduce reason-giving, even in the *Julie and Mark* scenario, but that our sub-sample of a sample of *N* = 412 did not have sufficient power to detect this effect. We cautiously present two reasons why this interpretation may be plausible. First, our equivalence test was sufficiently powered to detect equivalence at the level of *d* = .204, however, this failed to show equivalence. Second, all five pilot studies used the *Julie and Mark* dilemma, and while the results of these appear to be similarly inconclusive, the direction in the pattern of results remains consistent across all studies – that is the opposing pattern of results has not been shown in any study. None of the studies conducted showed an increase in reason-giving under cognitive load (even a non-significant increase).  

We note that while we did not find any significant differences in responding to the critical slide depending on performance for the cognitive load task, neither did we find evidence of equivalence. It is plausible that the quality of engagement with the secondary task will impact the influence of this secondary task on a moral judgment task, and this provides a further avenue for future research. 

It may be possible that some of the observed variability in our results can be attributed to methodological limitations. Classic studies of dual-process conflict are characterized by binary response options [an intuitive response contrasted with a deliberative response; @evans_resolution_2007], whereas our studies included three response options that varied in their relative amount of deliberation. As such the dumbfounding paradigm is more complex than classic binary response paradigms, and cognitive load manipulations may not be well suited for this additional complexity. It is also possible that this variability reflects a lack of statistical power to detect small effects for the specific scenario.

It is also possible that these results provide evidence that the conflict in dual-process explanation tested here is only part of the story, illustrating that moral dumbfounding displays high variability and context dependency [as with moral judgment more generally, see @mchugh_moral_2022]. For example, a further complication is that responses in the dumbfounding paradigm may involve competing intuitions. For example, participants may have intuitions relating to the nature of moral knowledge, such as moral judgments should be justifiable by reasons, that may become salient during the course of the study. This means that, in addition to experiencing a conflict between habitual and deliberative responding, participants may also experience competing intuitions. The relative salience of these competing intuitions may depend on a range of factors, including features of the scenario (e.g., severity/seriousness of the transgression, the kind of transgression), features of the characters in the scenario, personal familiarity with discourse around scenario content, and other factors such as current goals. Future research should unpack the influences of these competing intuitions.

One interesting finding that emerged that was not hypothesized was the apparent influence of cognitive load on participants' judgements. Under cognitive load, participants were significantly less harsh in their judgments (note that this appears to reflect judgments of lower extremity rather than a change in the valence of participants’ judgments). This was true for both initial judgments and revised judgments, suggesting that this is more than just an increased receptiveness to the counter-arguments under cognitive load (initial judgments were made before any counterarguments were presented). Future research should follow up on this finding, and investigate the influence of cognitive load on moral judgments more generally, e.g., does it only influence specific kinds of judgments (such as utilitarian judgments specifically, see Greene et al., 2008).   

Our findings have relevance for society more broadly. Moral considerations inform a range of behaviors and decisions, both at the individual level and at the societal level (Sinnott-Armstrong et al., 2010). It is likely that moral dumbfounding may be a contributing factor to moral disagreement on contentious issues. Our studies provide evidence that dumbfounding may be more prevalent in situations that constrain people’s ability to engage in deliberation. In practice, this suggests that when discussing contentious moral issues, disagreement through dumbfounding may be reduced by ensuring conditions suitable for deliberation (e.g., avoiding emotionally charged, high-pressure environments). Future research should build on this to test experimental manipulations that may help to reduce dumbfounding. Such a program of research may lead to the development of practical interventions that can reduce instances of dumbfounding in real-world situations. Examples of relevant experimental manipulations may draw on approaches such as construal level theory to encourage more abstract reasoning, e.g., through increased psychological/temporal distancing (e.g., Liberman et al., 2002). We note that attempts to test this will be similarly constrained by the methodological considerations identified above (three response options, competing intuitions).

While the studies presented here were in line with our theoretical predictions, we note that our samples were either student or online participants from Westernized countries, limiting the generalizability of our findings. While emerging research suggests that dumbfounding is observed in certain non-WEIRD populations [@mchugh_just_2021], future research should test if the explanation tested here generalizes beyond Western contexts.

# Conclusion
Moral dumbfounding occurs when people stubbornly maintain a moral judgment, even without reasons to support their judgments. To date, there are few studies that consider the causes of moral dumbfounding. Here, we test the idea that moral dumbfounding is more likely to occur when an individual is experiencing greater demands on their cognitive system, leaving less cognitive resources available for reasoning in complex moral dilemmas. The findings from the present research show that moral dumbfounding is more likely to occur under cognitive load, at least in some contexts. While these findings add new knowledge to the literature on moral dumbfounding, they also highlight the complexities of moral judgments. Further research is needed to better understand the factors that lead to dumbfounding, and, ultimately, how it might be reduced.





















