---
title             : "Study S2"
shorttitle        : "Cognitive Load and Moral Dumbfounding"
author:
  - name          : "Blinded"
    affiliation   : "1"
    corresponding : yes    # Define only one corresponding author
    address       : "Blinded"
    email         : "Blinded"
  - name          : "Blinded"
    affiliation   : "2"
  - name          : "Blinded"
    affiliation   : "1"
  - name          : "Blinded"
    affiliation   : "1"
affiliation:
  - id            : "1"
    institution   : "Blinded"
  - id            : "2"
    institution   : "Blinded"
author_note: |
  All procedures performed in studies involving human participants were approved by institutional research ethics committee and conducted in accordance with the Code of Professional Ethics of the Psychological Society of Ireland, and with the 1964 Helsinki declaration and its later amendments or comparable ethical standards. Informed consent was obtained from all individual participants included in the study. The authors declare that there are no potential conflicts of interest with respect to the research, authorship, and/or publication of this article. All authors consented to the submission of this manuscript.
abstract: |
  Six studies etc.
keywords          : "keywords"
wordcount         : "TBC"
bibliography: "../resources/bib/My Library.bib"
csl: "../resources/bib/apa6.csl"
figsintext        : yes
figurelist        : no
tablelist         : no
footnotelist      : no
lineno            : no
toc               : false
lang              : "en-US"
documentclass     : "apa7"
output:
  papaja::apa6_pdf
editor_options: 
  chunk_output_type: console
---

```{r S2setup_cogload, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
knitr::opts_chunk$set(include = FALSE)
# knitr::opts_chunk$set(fig.path='figure/graphics-', 
#                       cache.path='cache/graphics-', 
#                       fig.align='center',
#                       external=TRUE,
#                       echo=FALSE,
#                       warning=FALSE,
#                       fig.pos='H'
# )
```

```{r S2load_libraries_cogload}
rm(list = ls())
library(citr)
#install.packages("sjstats")
library(plyr)
library(foreign)
library(car)
library(desnum)
library(ggplot2)
library(extrafont)
#devtools::install_github("crsh/papaja")
library(papaja)
#library("dplyr")
library("afex")
library("tibble")
library(scales)
#install.packages("metap")
library(metap)
library(pwr)
library(lsr)
#install.packages("sjstats")
library(sjstats)
library(DescTools)
#inatall.packages("ggstatsplot")
#library(ggstatsplot)
library(VGAM)
library(nnet)
library(mlogit)
library(reshape2)
#install.packages("powerMediation")
library("powerMediation")
#install.packages("gridExtra")
library(gridExtra)

#source("load_all_data.R")

#devtools::install_github("benmarwick/wordcountaddin")
#library(wordcountaddin)
#wordcountaddin::text_stats("cogload_1to5_25Sept19.Rmd")
#getwd()
```


```{r S2apriori_power_analyses_cogload}

pwr.chisq.test(w=.35,df=(3-1),sig.level = .05, power=.8)
pwr.chisq.test(w=.21,df=(3-1),sig.level = .05, power=.8)
pwr.chisq.test(w=.07,df=(3-1),sig.level = .05, power=.8)
 
# https://www.real-statistics.com/chi-square-and-f-distributions/effect-size-chi-square/

```

\newpage

# Study S2: Dot-Pattern Task (Online Sample)

Study S1 demonstrated interesting variability in responses to the critical slide depending on cognitive load. The aim of Study S2 was to assess the replicability of the results of Study S1, using an online sample. In Study S1, the experimenter was in the room with the participants. This made it more difficult for participants to cheat on the memory task. This is not possible with an online sample. An alternative cognitive load manipulation was taken from De Neys and Schaeken [@deneys_when_2007], whereby a dot pattern is briefly presented to participants, and participants are required to reproduce the dot pattern at a later stage.

```{r S2load data set Study S2}
#### load data set 1 ####

rm(list = ls())

load("../loaded_data/two.RData")
df3 <- study_2



```
## Study S2: Method
### Study S2: Participants and design
Study S2 was a between subjects design.  The dependent variable was response to the critical slide.  The independent variable was cognitive load with two levels: high and low.  Need for Cognition [@cacioppo_need_1982; @petty_efficient_1984] was included as a potential correlate and moderator variable. 

A total sample of `r length(df3$InCS)` participants (`r sum(df3$gender=="Female")` female, `r sum(df3$gender=="Male")` male; *M*~age~ = `r round(mean(df3$age),digits=2)`, min = `r min(df3$age)`, max = `r max(df3$age)`, *SD* = `r round(sd(df3$age),digits=2)`) took part.  Participants in this sample were recruited using Amazon's MTurk [@amazonwebservicesinc._amazon_2016].  Participants were paid $0.50 for their participation.  Participants were recruited from English speaking countries or from countries where residents generally have a high level of English (e.g., The Netherlands, Denmark, Sweden).

### Study S2: Procedure and materials
Data were collected using an online questionnaire. Materials were largely the same as in Study S1, with a change to the cognitive load manipulation. Cognitive load was manipulated using a dot-pattern memory task [@deneys_when_2007].

Participants were presented with a 3 x 3 grid containing a dot pattern. This image disappeared after one second. Participants then answered a question relating to the moral judgement task. Following this, participants were asked to reproduce the dot-pattern. All participants took part in the memory task, and cognitive load was manipulated by varying the complexity of the patterns presented [@deneys_when_2007]. The control group were presented with simple patterns, containing three dots in a line, while the experimental group were presented with more complex dot patterns containing 4 dots, see Figure\ \@ref(fig:S2dotpattern).

```{r}


x <- c(10,20,30,30)
y <- c(10,30,10,20)
x <- x - 5
y <- y - 5



#rbind(x,y)
z <- cbind.data.frame(x,y)
z$diff <- rep("b",length=length(z$x))

x <- c(10,10,10)
y <- c(10,20,30)
x <- x - 5
y <- y - 5



#rbind(x,y)
z2 <- cbind.data.frame(x,y)
z2$diff <- rep("a",length=length(z2$x))

z3 <- rbind(z,z2)
#z3
#rm(g)
g <- ggplot(z3, aes(x=x,y=y)) +
 geom_point(size=8) +
 xlab(NULL) + ylab(NULL) + 
 scale_x_continuous(breaks = c(10,20),
                            labels = NULL, limits = c(1, 29)) +
#g <- g + scale_x_continuous(breaks = c(0,10,20,30), labels = NULL, limits = c(0, 30))
 scale_y_continuous(breaks = c(10,20),
                            labels = NULL, limits = c(1, 29))+
  facet_grid(.~diff,switch = 'x')+
 theme(plot.title=element_text(#family="Times",
                               size=12),
               legend.text=element_text(#family="Times", 
                                        size=8),
               legend.title=element_text(#family="Times",
                                         size=12),
               axis.text=element_text(#family="Times",
                                      size=8),
               axis.title=element_text(#family="Times", 
                 size=12),
               panel.background = element_rect(fill = "white",
                                               colour = NA),
               panel.border = element_rect(fill = NA, size = 1,
                                           colour = "black"),
               panel.grid.major = element_line(colour = "black"),
               panel.grid.minor = element_line(colour = "white",
                                               size = 0.25),
               axis.ticks.length = unit(0,"cm"),
       plot.margin = NULL,
       strip.background = element_rect(fill = NA, size = 1,
                                           colour = "white"),
       strip.text = element_text(#family = "Times",
                                 size = 16),
       panel.spacing = unit(4, "lines"))

```


```{r S2dotpattern,fig.cap="Sample dot patterns - more simple for the control group (a) and higher complexity for the experimental condition (b)",include=TRUE,fig.height=2, fig.width=6}

suppressWarnings(print(g))

```

Study S2 proceeded in much the same way as Study S1. There were four target questions during which participants were engaged in the memory task. A different pattern was presented before each of the following: the initial judgement, the initial opportunity to provide reasons, the critical slide, and the revised judgement. After each of these questions participants were required to reproduce the pattern. As in Study S1, dumbfounding was measured using the critical slide.


```{r S2s1change in judgement}

# create variables for reporting t.tests
t <- t.test(df3$InJu1,df3$InJu2, paired = TRUE)

#chisquare test function

custom_chi <- function(x,y){
  a <- length(x)
  b <- length(y)
  c <- rep(1, a)
  d <- rep(2, b)
  e <- c(c,d)
  f <- c(x, y)
  
  g <- data.frame(e,f)
  h <- table(g$e,g$f)
  suppressWarnings(chisq.test(h))
}

c <- suppressWarnings(custom_chi(df3$InJu1,df3$InJu2))

changed_num <- function(x, judgement_1, judgement_2){
  b <- b <- x[which(x$Ju1_bin==judgement_1 & x$Ju2_bin==judgement_2),]
  length(b$Ju1_bin)
  
}

tot_changed_num <- function(x, query){
  
  c <- cbind.data.frame(x$Ju1_bin[which(x$Ju1_bin!=x$Ju2_bin)],x$Ju2_bin[which(x$Ju1_bin!=x$Ju2_bin)])
  colnames(c) <- c("initial_judgement","revised_judgement")
  
  c
  if(query == "table") print(c)
  if(query == "total") print(length(c$initial_judgement))}


tot_changed_table <- function(x){
  
  c <- cbind.data.frame(x$Ju1_bin[which(x$Ju1_bin!=x$Ju2_bin)],x$Ju2_bin[which(x$Ju1_bin!=x$Ju2_bin)])
  colnames(c) <- c("Initial Judgment","Revised Judgment")
  
  c
  }

change_table <- tot_changed_table(df3)

```



```{r S2checkingchanges2}

sum(df3$InCS!="There is nothing wrong."&df3$Ju1_bin!="wrong")

t_j1 <- t.test(df3$InJu1 ~ df3$condition)
d_j1 <- cohensD(df3$InJu1 ~ df3$condition)
#t_j1 <- t.test(college$InJu1 ~ college$condition)
#t_paragraph(college$InJu1, college$condition, "initial judgement")
#t_paragraph(one$InJu1, one$condition, "initial judgement")
#t_paragraph(two$InJu1, two$condition, "initial judgement")
#t_paragraph(three$InJu1, three$condition, "initial judgement")

#

c <- chisq.test(table(df3$InCS,df3$condition))
w <- sqrt(c[]$statistic/length(df3$gender))
pw <- pwr.chisq.test(w=w,N=length(df3$InCS),df=(3-1),sig.level = .05)


```


```{r S2checkingchanges1}

t_j1 <- t.test(df3$InJu1 ~ df3$condition)
d_j1 <- cohensD(df3$InJu1 ~ df3$condition)

t_paragraph(df3$InJu1, df3$condition, "initial judgement")
#t_paragraph(one$InJu1, one$condition, "initial judgement")
#t_paragraph(two$InJu1, two$condition, "initial judgement")
#t_paragraph(three$InJu1, three$condition, "initial judgement")


t_j2 <- t.test(df3$InJu2 ~ df3$condition)
d_j2 <- cohensD(df3$InJu2 ~ df3$condition)

t_paragraph(df3$InJu2, df3$condition, "revised judgement")
#t_paragraph(one$InJu1, one$condition, "initial judgement")
#t_paragraph(two$InJu1, two$condition, "initial judgement")
#t_paragraph(three$InJu1, three$condition, "initial judgement")

t_paired_paragraph(df3$InJu1,df3$InJu2, "judgment")
t_j3 <- t.test(df3$InJu1,df3$InJu2,paired = TRUE)
d_j3 <- cohensD(df3$InJu1,df3$InJu2, method = "paired")


```

## Study S2: Results
`r numbers2words_cap1(length(df3$Ju1_bin[df3$Ju1_bin=="wrong"]))` participants (`r round(((length(df3$Ju1_bin[df3$Ju1_bin=="wrong"])/length(df3$Ju1_bin))*100), digits=2)`%) rated the behavior of Julie and Mark as wrong initially, and `r numbers2words(length(df3$Ju2_bin[df3$Ju2_bin=="wrong"]))` participants (`r round(((length(df3$Ju2_bin[df3$Ju2_bin=="wrong"])/length(df3$Ju2_bin))*100), digits=2)`%) rated the behavior as wrong at the end of the task. Initial ratings (*M* = `r round(mean(df3$InJu1), digits = 2)`, *SD* = `r round(sd(df3$InJu1), digits = 2)`) were significantly more severe than revised ratings (*M* = `r round(mean(df3$InJu2), digits = 2)`, *SD* = `r round(sd(df3$InJu2), digits = 2)`), *t*(`r t_j3$parameter`) = `r t_j3$statistic`, *p* `r paste(p_report(t_j3$p.value))`; *d* = `r round(d_j3, digits=2)`. Inspection of the binned judgments revealed that `r numbers2words(tot_changed_num(df3, "total"))` participants changed the valence of their judgments, and all but one of these involved one judgment that was neutral (see Table\ \@ref(tab:tabS2change)). 


```{r tabs2change in judgement}


##### Study S2 #####

# create variables for reporting t.tests
t <- t.test(df3$InJu1,df3$InJu2, paired = TRUE)

#chisquare test function

custom_chi <- function(x,y){
  a <- length(x)
  b <- length(y)
  c <- rep(1, a)
  d <- rep(2, b)
  e <- c(c,d)
  f <- c(x, y)
  
  g <- data.frame(e,f)
  h <- table(g$e,g$f)
  suppressWarnings(chisq.test(h))
}

c <- suppressWarnings(custom_chi(df3$InJu1,df3$InJu2))

changed_num <- function(x, judgement_1, judgement_2){
  b <- b <- x[which(x$Ju1_bin==judgement_1 & x$Ju2_bin==judgement_2),]
  length(b$Ju1_bin)
  
}

tot_changed_num <- function(x, query){
  
  c <- cbind.data.frame(x$Ju1_bin[which(x$Ju1_bin!=x$Ju2_bin)],x$Ju2_bin[which(x$Ju1_bin!=x$Ju2_bin)])
  colnames(c) <- c("Initial Judgment","Revised Judgment")
  
  c
  if(query == "table")
    print(c)
  if(query == "total") print(length(c$initial_judgement))}


tot_changed_table <- function(x){
  
  c <- cbind.data.frame(x$Ju1_bin[which(x$Ju1_bin!=x$Ju2_bin)],x$Ju2_bin[which(x$Ju1_bin!=x$Ju2_bin)])
  colnames(c) <- c("Initial Judgment","Revised Judgment")
  
  c
  }

change_table <- tot_changed_table(df3)
change_table <- table(change_table)
change_table <- as.data.frame(change_table)
change_table <- change_table[which(change_table$Freq!=0),]
change_table <- change_table[order(change_table$Initial.Judgment, change_table$Revised.Judgment), ]
colnames(change_table) <- c("Initial Judgment","Revised Judgment", "Total Changed")
#order(change_table$Initial.Judgment)
```



```{r tabS2change,results = 'asis', include=TRUE}


apa_table(
   change_table
   , align = c("c", "c")
   , caption = "Study S2 – Changes in Jugment"
   #, added_stub_head = "Response to critical slide"
   #, col_spanners = makespanners()
   #, note = "* = sig. at \\emph{p} < .05; ** = sig. at \\emph{p} < .001"
   , escape = FALSE
   
)

```



Participants who selected the admission of not having reasons on the critical slide were identified as dumbfounded.  `r numbers2words_cap1(length(df3$InCS[which(df3$InCS=="It's wrong but I can't think of a reason.")]))` participants (`r round((length(df3$InCS[which(df3$InCS=="It's wrong but I can't think of a reason.")])/(length(df3$InCS)))*100, digits=2)`%) selected "It's wrong but I can't think of a reason".  `r numbers2words_cap1(length(df3$InCS[which(df3$InCS=="It's wrong and I can provide a valid reason.")]))` participants (`r round((length(df3$InCS[which(df3$InCS=="It's wrong and I can provide a valid reason.")])/(length(df3$InCS)))*100,digits=2)`%) selected “It's wrong and I can provide a valid reason”; and `r numbers2words(length(df3$InCS[which(df3$InCS=="There is nothing wrong.")]))` participants (`r round((length(df3$InCS[which(df3$InCS=="There is nothing wrong.")])/(length(df3$InCS)))*100,digits=2)`%) selected “There is nothing wrong”.

A chi-squared test for independence revealed no association between experimental condition and response to the critical slide, $\chi$^2^(`r c$parameter`, *N* = `r length(df3$Ju1_bin)`) = `r round(c$statistic, digits=3)`, *p* `r paste(p_report(c$p.value))`, *V* = `r w`, the observed power was `r pw$power`.  The responses to the critical slide for the experimental group (*N* = `r sum(df3$condition=="cog_load")`) and the control group (*N* = `r sum(df3$condition=="control")`) are displayed in Figure\ \@ref(fig:S2figboth) and Table\ \@ref(tab:tabS2tab1dumb1all).  



```{r}

df3$InCS <- df3$InCS

test <- as.data.frame.matrix((table(df3$InCS,df3$condition)))
#`rownames<-`(test, c("nothing wrong","no reason","reasons"))
test <- as.matrix((test))
test1 <- cbind(test[,1],test[,2])
test2 <- `colnames<-`(test1, c("cognitive load","control"))

tb_count_perc <- function(x){
  tc <- table(x$InCS,x$condition)
  cbind(tc[,1],paste0(round(tc[,1]/sum(x$condition=="cog_load")*100),"%"),
        tc[,2],paste0(round(tc[,2]/sum(x$condition=="control")*100),"%"))
  }
  
tb_count_perc_eng <- function(x){
  tc <- table(x$InCS,x$engaged)
  cbind(tc[,1],paste0(round(tc[,1]/sum(x$engaged=="engaged")*100),"%"),
        tc[,2],paste0(round(tc[,2]/sum(x$engaged=="not engaged")*100),"%"))
  }
  
test <- tb_count_perc(df3)
test <- as.data.frame(test)
colnames(test) <- c("N","\\%","N","\\%")

test_condition <- test
  


test <- as.data.frame.matrix((table(df3$InCS,df3$engaged)))
#`rownames<-`(test, c("nothing wrong","no reason","reasons"))
test <- as.matrix((test))
test1 <- cbind(test[,1],test[,2])
test2 <- `colnames<-`(test1, c("cognitive load","control"))

tb_count_perc <- function(x){
  tc <- table(x$InCS,x$condition)
  cbind(tc[,1],paste0(round(tc[,1]/sum(x$condition=="cog_load")*100),"%"),
        tc[,2],paste0(round(tc[,2]/sum(x$condition=="control")*100),"%"))
  }
  
tb_count_perc_eng <- function(x){
  tc <- table(x$InCS,x$engaged)
  cbind(tc[,1],paste0(round(tc[,1]/sum(x$engaged=="engaged")*100),"%"),
        tc[,2],paste0(round(tc[,2]/sum(x$engaged=="not engaged")*100),"%"))
  }
  
test <- tb_count_perc_eng(df3)
test <- as.data.frame(test)
colnames(test) <- c("N","\\%","N","\\%")

test_engaged <- test
  
test <- rbind.data.frame(test_condition,test_engaged)
Response <- c("Reasons", "Dumbfounded", "Nothing Wrong"
              ,"Reasons", "Dumbfounded", "Nothing Wrong")
Measure <- c("Manipulation Only","","","Engagement","","")

test <- cbind.data.frame(Measure, Response, test)

test <- `rownames<-`(test, NULL)

makespanners <- function(){
  cog_load <- c(3,4)
  control <- c(5,6)
  spans <- list(cog_load,control)
  names(spans) <- c("Cognitive Load","Control")
  spans
}

#test <- tb_count_perc(df3)
#tb_count_perc(df3a)




```


```{r tabS2tab1dumb1all,results = 'asis', include=TRUE}


apa_table(
   test
   , align = c("l", "l", "c", "c", "c", "c")
   , caption = "Study S2 – Response to the critical slide depending on cognitive load/engagement"
   #, added_stub_head = "Response to critical slide"
   , col_spanners = makespanners()
   #, note = "* = sig. at \\emph{p} < .05; ** = sig. at \\emph{p} < .001"
   , escape = FALSE
   
)

```



```{r S2prepch5S2fig2}



y <- table(df3$InCS,df3$condition)
#y <- table(df3$InCS,df3$engaged)
y <- as.data.frame(y)
#colnames(y) <- c("condition","InCS","Freq")
colnames(y) <- c("InCS","condition","Freq")

z <- as.data.frame(table(df3$condition,df3$InCS)/length(df3$gender)*2)

z <- rbind(as.data.frame(table(df3$InCS[which(df3$condition=="cog_load")])/
                           length(df3$InCS[which(df3$condition=="cog_load")])),
           as.data.frame(table(df3$InCS[which(df3$condition=="control")])/
                           length(df3$InCS[which(df3$condition=="control")])))



perc <- z$Freq
test <- cbind(y,perc)



# 
# y <- table(df3$condition,df3$Dumb_incl_string)
# y <- as.data.frame(y)
 colnames(y) <- c("InCS","condition","Freq")

# z <- as.data.frame(table(df3$condition,df3$Dumb_incl_string)/length(df3$gender)*2)
# perc <- z$Freq
# test <- cbind(y,perc)
# test$condition
# test
 


ab_graph <- function(){
  a <- df3[which(df3$condition==levels(as.factor(df3$condition))[1]),]
  b <- df3[which(df3$condition==levels(as.factor(df3$condition))[2]),]
  #levels(as.factor(df3$condition))[1]
  
  ay <- as.data.frame(table(a$InCS,a$condition))
  by <- as.data.frame(table(b$InCS,b$condition))
  
  aperc <- ay$Freq/length(a$gender)
  ay <- cbind(ay,aperc)
  colnames(ay) <- c("InCS","condition","Freq","perc")
  
  bperc <- by$Freq/length(b$gender)
  by <- cbind(by,bperc)
  colnames(by) <- c("InCS","condition","Freq","perc")
  
  c <- rbind(ay,by)
  
  c
}

test <- ab_graph()
test$measure <- rep("Cognitive Load Manipulation", length(test$InCS))

test_condition <- test


rm(x,y)
```


```{r}

x <- df3

se_fun <- function(a,b){
  k <- length(a$gender)
  n <- length(b$gender)
  
  pbar <- k/n
  a$pbar <- pbar
  a$se = sqrt(pbar * (1 - pbar)/n)
  a}
# https://www.r-tutor.com/elementary-statistics/interval-estimation/interval-estimate-population-proportion

y <- rbind(
  se_fun(x[which(x$condition=="control"&x$InCS=="It's wrong and I can provide a valid reason."),]
         ,x[which(x$condition=="control"),])
  ,se_fun(x[which(x$condition=="control"&x$InCS=="There is nothing wrong."),]
          ,x[which(x$condition=="control"),])
  ,se_fun(x[which(x$condition=="control"&x$InCS=="It's wrong but I can't think of a reason."),]
          ,x[which(x$condition=="control"),])
  ,se_fun(x[which(x$condition=="cog_load"&x$InCS=="It's wrong and I can provide a valid reason."),]
          ,x[which(x$condition=="cog_load"),])
  ,se_fun(x[which(x$condition=="cog_load"&x$InCS=="There is nothing wrong."),]
          ,x[which(x$condition=="cog_load"),])
  ,se_fun(x[which(x$condition=="cog_load"&x$InCS=="It's wrong but I can't think of a reason."),]
          ,x[which(x$condition=="cog_load"),])
)

y1 <- y %>% select("InCS","condition","pbar","se")


test1 <- dplyr::left_join(test,y1, by = c("condition","InCS") )


test_condition <- test1

```

```{r S2ch5S2fig2criticalcondition, fig.cap="Study S2: Responses to critical slide for the experimental group (*N* = 51) and the control group (*N* = 49); (error bars represent standard error of the proportion)", include=FALSE}


g1 <- ggplot(test1, aes(x=reorder(InCS), y=perc, fill=factor(condition,labels=c("Cognitive load","Control")))) +
  scale_y_continuous(limits = c(-.03,1),
                     labels = percent_format()
  )+ 
  geom_col(position = "dodge",
           color="black",
           size=.2
  )+
  geom_errorbar(aes(ymin=perc-se, ymax=perc+se), width=.2,
               position=position_dodge(.9), color="black" #"#5a5a5a"
                 )+
  geom_text(#family = "Times",
            size=4.2,
            aes( label = scales::percent(perc, accuracy = 1),
                 y= perc ),
            stat= "identity",
            vjust = -.5,
            hjust = +1.1,
            position = position_dodge(.9),
            fontface='plain'
            )+
  geom_text(#family = "Times", 
            size=4.2,
            aes(label = format(Freq),
                y= -2*(..count../100)/(..count..)),
            stat= "count",
            position = position_dodge(0.9),
            #vjust = -.05,
            fontface='plain'
            )+
  geom_errorbar(aes(ymin=perc-se, ymax=perc+se), width=.2,
               position=position_dodge(.9), color="black" #"#5a5a5a"
                 )+
  xlab("Response to Critical Slide") +
  ylab("Percentage of participants selecting each response")+
  scale_x_discrete(labels=c("Reasons", "Dumbfounded","Nothing Wrong")) +
  scale_fill_grey(start = .5, end = .8) +
  labs(fill="Condition") +
  #theme_apa() +
  theme_bw() +
  theme(panel.border = element_blank(),
        axis.line = element_line(size = .2),
        strip.background  = element_blank(),
        panel.grid = element_blank(),
        plot.title=element_text(#family="Times",
                                size=12
                                ),
        legend.text=element_text(#family="Times",
                                 size=8
                                 ),
        legend.title=element_text(#family="Times",
                                    size=10
                                 ),
        axis.text=element_text(#family="Times",
                                 colour = "black",
                                 size=8
                                 ),
        axis.ticks.x = element_blank(),
        axis.title=element_text(#family="Times",
                                  size=12
                                  ),
        strip.text=element_text(#family = "Times",
                                  size = 12
                                  ),
        #strip.background = element_rect(fill = "white"),
        legend.position="right")





#rm(a,b,c)
# 
# g <- ggplot(df3, aes(x=InCS, fill=factor(condition,labels=c("Cognitive load","Control"))))
# g <- g + geom_bar(aes(y=..count..), position = position_dodge(), color="black")
# g <- g + xlab("Response to critical slide")
# #g <- g + ggtitle("Dumbfounding and Cognitive load")
# g <- g + scale_x_discrete(labels=c("nothing wrong", "no reason", "valid reason"))
# g <- g + scale_fill_grey(start = .5, end = .8)+ theme_bw()
# g <- g + labs(fill="Condition") 
# #grid.gedit("GRID.text",gp=gpar(fontfamily="serif"))
# g <- g + geom_text(family = "Times", aes(label = format(..count..),y= ..count.. ), stat= "count", vjust = 1.6, position = position_dodge(0.9))
# 
# g + theme(plot.title=element_text(family="Times", size=12), legend.text=element_text(family="Times", size=8), legend.title=element_text(family="Times", size=12), axis.text=element_text(family="Times", size=8), axis.title=element_text(family="Times", size=12))
# rm(g)

df4 <- df3[which(df3$engaged=="engaged"),]
df5 <- df3[which(df3$engaged=="not engaged"),]

# table(df3$InCS,df3$engaged)


```


```{r S2ch5prepengaged}

df3 <- one

#y <- table(df3$InCS,df3$condition)
y <- table(df3$InCS,df3$engaged)
y <- as.data.frame(y)
#colnames(y) <- c("condition","InCS","Freq")
colnames(y) <- c("InCS","condition","Freq")

z <- as.data.frame(table(df3$condition,df3$InCS)/length(df3$gender)*2)



z <- rbind(as.data.frame(table(df3$InCS[which(df3$engaged=="engaged")])/
                           length(df3$InCS[which(df3$engaged=="engaged")])),
           as.data.frame(table(df3$InCS[which(df3$engaged=="not engaged")])/
                           length(df3$InCS[which(df3$engaged=="not engaged")])))


perc <- z$Freq
test <- cbind(y,perc)

test$measure <- rep("Engaged", length(test$InCS))

test_engaged <- test

```



```{r}



se_fun <- function(a,b){
  k <- length(a$gender)
  n <- length(b$gender)
  
  pbar <- k/n
  a$pbar <- pbar
  a$se = sqrt(pbar * (1 - pbar)/n)
  a}
# https://www.r-tutor.com/elementary-statistics/interval-estimation/interval-estimate-population-proportion

y <- rbind(
  se_fun(  x[which(x$engaged=="not engaged"&x$InCS=="It's wrong and I can provide a valid reason."),]
          ,x[which(x$engaged=="not engaged"),])
  ,se_fun( x[which(x$engaged=="not engaged"&x$InCS=="There is nothing wrong."),]
          ,x[which(x$engaged=="not engaged"),])
  ,se_fun( x[which(x$engaged=="not engaged"&x$InCS=="It's wrong but I can't think of a reason."),]
          ,x[which(x$engaged=="not engaged"),])
  ,se_fun( x[which(x$engaged=="engaged"&x$InCS=="It's wrong and I can provide a valid reason."),]
          ,x[which(x$engaged=="engaged"),])
  ,se_fun( x[which(x$engaged=="engaged"&x$InCS=="There is nothing wrong."),]
          ,x[which(x$engaged=="engaged"),])
  ,se_fun( x[which(x$engaged=="engaged"&x$InCS=="It's wrong but I can't think of a reason."),]
          ,x[which(x$engaged=="engaged"),])
)


y1 <- y %>% select("InCS","engaged","pbar","se")
y1 <- `colnames<-`(y1, c("InCS","condition","pbar","se"))

test1 <- dplyr::left_join(test,y1, by = c("condition","InCS"), multiple="all" )

test_engaged <- test1


```

```{r S2ch5S2fig2criticalengaged, fig.cap="Study S2: Responses to critical slide depending on engagement (*N* = 56) or non-engagement (*N* = 44) with the memory task; (error bars represent standard error of the proportion)", include=FALSE}


g2 <- ggplot(test1, aes(x=InCS, y=perc, fill=factor(condition,labels=c("Engaged","Not Engaged")))) +
  scale_y_continuous(limits = c(-.03,1),
                     labels = percent_format()
  )+ 
  geom_col(position = "dodge",
           color="black",
           size=.2
  )+
  geom_errorbar(aes(ymin=perc-se, ymax=perc+se), width=.2,
               position=position_dodge(.9), color="black" #"#5a5a5a"
                 )+
  geom_text(#family = "Times",
            size=4.2,
            aes( label = scales::percent(perc, accuracy = 1),
                 y= perc ),
            stat= "identity",
            vjust = -.5,
            hjust = +1.1,
            position = position_dodge(.9),
            fontface='plain'
            )+
  geom_text(#family = "Times", 
            size=4.2,
            aes(label = format(Freq),
                y= -2*(..count../100)/(..count..)),
            stat= "count",
            position = position_dodge(0.9),
            #vjust = -.05,
            fontface='plain'
            )+
  geom_errorbar(aes(ymin=perc-se, ymax=perc+se), width=.2,
               position=position_dodge(.9), color="black" #"#5a5a5a"
                 )+
  xlab("Response to Critical Slide") +
  ylab("Percentage of participants selecting each response")+
  scale_x_discrete(labels=c("Reasons", "Dumbfounded","Nothing Wrong")) +
  scale_fill_grey(start = .5, end = .8) +
  labs(fill="Condition") +
  #theme_apa() +
  theme_bw() +
  theme(panel.border = element_blank(),
        axis.line = element_line(size = .2),
        strip.background  = element_blank(),
        panel.grid = element_blank(),
        plot.title=element_text(#family="Times",
                                size=12
                                ),
        legend.text=element_text(#family="Times",
                                 size=8
                                 ),
        legend.title=element_text(#family="Times",
                                    size=10
                                 ),
        axis.text=element_text(#family="Times",
                                 colour = "black",
                                 size=8
                                 ),
        axis.ticks.x = element_blank(),
        axis.title=element_text(#family="Times",
                                  size=12
                                  ),
        strip.text=element_text(#family = "Times",
                                  size = 12
                                  ),
        #strip.background = element_rect(fill = "white"),
        legend.position="right")




#rm(a,b,c)
# 
# g <- ggplot(df3, aes(x=InCS, fill=factor(condition,labels=c("Cognitive load","Control"))))
# g <- g + geom_bar(aes(y=..count..), position = position_dodge(), color="black")
# g <- g + xlab("Response to critical slide")
# #g <- g + ggtitle("Dumbfounding and Cognitive load")
# g <- g + scale_x_discrete(labels=c("nothing wrong", "no reason", "valid reason"))
# g <- g + scale_fill_grey(start = .5, end = .8)+ theme_bw()
# g <- g + labs(fill="Condition") 
# #grid.gedit("GRID.text",gp=gpar(fontfamily="serif"))
# g <- g + geom_text(family = "Times", aes(label = format(..count..),y= ..count.. ), stat= "count", vjust = 1.6, position = position_dodge(0.9))
# 
# g + theme(plot.title=element_text(family="Times", size=12), legend.text=element_text(family="Times", size=8), legend.title=element_text(family="Times", size=12), axis.text=element_text(family="Times", size=8), axis.title=element_text(family="Times", size=12))
# rm(g)

#(1-pnorm(3.30))*2

```


```{r}
test1 <- rbind.data.frame(test_condition,test_engaged)
test1$condition <- 
  car::recode(test1$condition
              ,"'engaged'='cog_load';'not engaged'='control'")

```

```{r}
g <- ggplot(test1, aes(x=InCS, y=perc
                  , fill=factor(condition
                                ,labels=c("Cognitive load\n(engaged)"
                                          ,"Control\n(not engaged)")
                                             ))) +
  facet_wrap(~measure,scales='free')+
  scale_y_continuous(limits = c(-.03,1),
                     labels = percent_format()
  )+ 
  geom_col(position = "dodge",
           color="black",
           size=.2
  )+
  geom_errorbar(aes(ymin=perc-se, ymax=perc+se), size=.1, width=.1,
               position=position_dodge(.9), color=#"black" #
                 "#5a5a5a"
                 )+
  geom_text(#family = "Times",
            size=1.5,
            aes( label = scales::percent(perc, accuracy = 1),
                 y= perc ),
            stat= "identity",
            vjust = -.5,
            hjust = +1.1,
            position = position_dodge(.9),
            fontface='plain'
            )+
  geom_text(#family = "Times", 
            size=1.8,
            aes(label = format(Freq),
                y= -2.5*(..count../100)/(..count..)),
            stat= "count",
            position = position_dodge(0.9),
            #vjust = -.05,
            fontface='plain'
            ) +
  xlab("Response to Critical Slide") +
  ylab("Percentage of participants selecting each response")+
  scale_x_discrete(labels=c("Reasons", "Dumbfounded","Nothing Wrong")) +
  scale_fill_grey(start = .5, end = .8) +
  labs(fill="Condition") +
  # 
  # geom_text(#family = "Times", 
  #           size=4.2,
  #           aes( label = scales::percent(test$perc),
  #                y= test$perc ),
  #           stat= "identity",
  #           vjust = -.5,
  #           position = position_dodge(.9),
  #           fontface='plain'
  #           )+
  #theme_apa() +
  theme_bw() +
  theme(panel.border = element_blank(),
        axis.line = element_line(size = .2),
        strip.background  = element_blank(),
        panel.grid = element_blank(),
        plot.title=element_text(#family="Times",
                                size=8
                                ),
        legend.text=element_text(#family="Times",
                                 size=6
                                 ),
        legend.title=element_text(#family="Times",
                                    size=8
                                    ),
        axis.text=element_text(#family="Times",
                               colour = "black",
                               size=6
                               ),
        axis.ticks.x = element_blank(),
        axis.title=element_text(#family="Times",
                                size=8
                                ),
        strip.text=element_text(#family = "Times",
                                  size = 8
                                  ),
        #  strip.background = element_rect(fill = "white"),
        legend.position="right")
```


```{r S2figboth, fig.cap="Study S2: Responses to critical slide for (left) the experimental group (N = 51) vs the control group (N = 49); and (right) depending on engagement (N = 56) or non-engagement (N = 44) with the memory task (error bars represent standard error of the proportion)", include=TRUE,fig.height = 3}


suppressWarnings(print(g))

```



```{r S2prepplottinglogit2}

df3 <- df3[which(is.na(df3$NFC)==FALSE),]

x <- df3$NFC
y <- as.numeric(df3$InCS)

m1 <- multinom(y ~ x)
# summary(m1)
newdata <- data.frame(x = seq(min(x), max(x), length.out = 100))
p1 <- predict(m1, newdata, type = "class")
p2 <- predict(m1, newdata, type = "probs")


logit_plot <- cbind.data.frame(newdata,p2)

logit_plot <- `colnames<-`(logit_plot, c("x","one_l","two_l","three_l"))
logit_plot <- melt(logit_plot, id="x")

```


```{r S2ggplotlogit2, fig.cap="Study S2: Probability of selecting each response to the critical slide depending on Need for Cognition", include=TRUE}


ggplot(logit_plot,
       aes(x=x, y=value,
           #color=factor(variable,labels=c("dumb","reason","nothing"))
           linetype=factor(variable,labels=c("Reasons","Dumbfounded","Nothing Wrong"))
           )) +
  geom_line()+
  xlab("Need for Cognition") + ylab("Predicted Probability") +
  scale_y_continuous(limits = c(0, 1)) + 
  #scale_color_discrete(name="Response to \nCritical Slide", labels=c("Dumbfounded","Nothing Wrong","Reasons"))+
  scale_linetype_discrete(name="Response to \nCritical Slide"
                          #, labels=c("Dumbfounded","Nothing Wrong","Reasons")
                          )+
  theme_bw() +
  theme(plot.title=element_text(#family="Times",
                                size=12
  ),
  legend.text=element_text(#family="Times",
                           size=8
  ),
  legend.title=element_text(#family="Times",
                            size=10
  ),
  axis.text=element_text(#family="Times",
                         colour = "black",
                         size=8
  ),
  axis.ticks.x = element_blank(),
  axis.title=element_text(#family="Times",
                          size=12
  ),
  strip.text=element_text(#family = "Times",
                          size = 12
  ),
  strip.background = element_rect(fill = "white"),
  legend.position="right")



```



It is possible that the difference in results observed between Study S1 and  Study S2 is due to the alternative manipulation of cognitive load employed. In Study S1, the control group did not engage in any task, however, adopting De Neys and Shaeken's procedure [-@deneys_when_2007], participants in the control group of Study S2 engaged in a memory task.  It is possible that simply engaging in a memory task led to differences in responses, and that level of difficulty (the manipulation that was employed) was irrelevant. Indeed, the responding to the critical slide in the control group in Study S2 is more similar to the responding in the experimental group in 1 than to the control group in Study S1. Furthermore, rates of successful reproduction of the dot patterns in Study S2 were much lower than reported by De Neys and Shaeken [-@deneys_when_2007]. It is likely that engagement with the memory task in Study S2 was not comparable to that observed by De Neys and Shaeken [-@deneys_when_2007], and this impacted the results. We propose that not engaging appropriately with the memory task undermines its efficacy as a cognitive load manipulation, and hypothesized that the effect of the cognitive load manipulation is related to the degree to which people engage with the manipulation. 

```{r S2preptableS2}
c <- chisq.test(table(df3$InCS,df3$engaged))
rownames(rbind(c$observed,c$expected,c$stdres))


ps <- function(y){
  if(as.numeric(sqrt( y*y) ) >3.3) print(paste0(y,"**"), quote = FALSE)
  else if(as.numeric(sqrt( y*y) ) >1.96) print(paste0(y,"*"), quote = FALSE)
  else print(y)}

x <- c$stdres
x <- round(x, digits = 2)

lapply(x, ps)

#c$stdres <- round(c$stdres,digits=3)
#c$stdres <- ps(c$stdres)

ps(x[1])
ps(x[2])
ps(x[3])

x <- `colnames<-`(
  cbind.data.frame(c(ps(x[1]),ps(x[2]),ps(x[3])),
                   c(ps(x[4]),ps(x[5]),ps(x[6]))),
  c("engaged","not engaged")
)

rownames(x) <- row.names(c$observed)  

y <- rbind(round(round(c$observed)), round(c$expected, digits = 2))

c(c$stdres[1])


res <- cbind(c("Observed count","","","Expected count","","","Standardised residuals","",""),
      c("Reasons","Dumbfounded","Nothing Wrong",
        "Reasons","Dumbfounded","Nothing Wrong",
        "Reasons","Dumbfounded","Nothing Wrong"),
      rbind(y,x)
      
      )

row.names(res) <- NULL
colnames(res) <- c("","","Engaged","Not Engaged")




```

```{r S2S2tab1dumb,results = 'asis', include=TRUE}


apa_table(
   res
   , align = c("l", "l", "c", "c", "c")
   , caption = "Study S2 – Observed counts, expected counts, and standardised residuals for each response to the critical slide depending on cognitive load"
   #, added_stub_head = "Response to critical slide"
   #, col_spanners = makespanners()
   , note = "* = sig. at \\emph{p} < .05; ** = sig. at \\emph{p} < .001"
   , escape = FALSE
   
)

```

To test this claim we developed a measure of engagement with the memory task. The memory task involved correctly placing dots in a 3 x 3 grid. For the scoring of this task, each of the nine places in the grid could be marked/not marked correctly or incorrectly, making 9 the total possible number of correct responses. If a person misplaced one dot in the pattern this would count for 2 incorrect places in the grid: the mark in the incorrect place, and the absence of a mark in the place it should have been. A participant who received a score of 7, could reasonably be taken to have engaged with the task, and simply made a slip. As such, this was taken as the cut-off point for identifying engagement.  This resulted in 56 participants being identified as engaging with the memory task, and 44 being identified as not engaging with the task.

```{r S2ch5S2dumbfoundingengaged}
c <- chisq.test(table(df3$InCS,df3$engaged))

w <- sqrt(c[]$statistic/length(df3$gender))
#w <- sqrt(2.464856/120)
pwr.chisq.test(w=w,df=(3-1),N=length(df3$InCS),sig.level = .05)
c[]$stdres
c[]

```

Using this engagement threshold, we tested if responses to the critical were associated with engagement with the memory task. A chi-squared test for independence revealed an association between engagement in the memory task and response to the critical slide, $\chi$^2^(`r c$parameter`, *N* = `r length(df3$Ju1_bin)`) = `r round(c$statistic, digits=3)`, *p* `r paste(p_report(c$p.value))`, *V* = `r w`, the observed power was `r pw$power`.  The responses to the critical slide for the experimental group (*N* = `r sum(df3$condition=="cog_load")`) and the control group (*N* = `r sum(df3$condition=="control")`) are displayed in Figure\ \@ref(fig:S2figboth).  The observed counts, expected counts and standardized residuals are displayed in Table\ \@ref(tab:S2S2tab1dumb).


```{r S2logit2}

#df3$InCS <- relevel(df3$InCS, ref = 2)

df3a <- mlogit.data(df3, choice = "InCS", shape = "wide")
InCSModel<-mlogit(InCS ~ 1 | NFC, data = df3a, reflevel = "It's wrong and I can provide a valid reason.")

summary_InCS_model <- summary(InCSModel)
summary_InCS_model$lratio$parameter
summary_InCS_model$lratio$statistic
summary_InCS_model$lratio$p.value

InCSModel$coefficients[3]
InCSModel$coefficients[4]

cox <- PseudoR2(multinom(InCS~NFC,df3), "all")

cox[3]
cox[4]
#PseudoR2(x, "all")
#summary_InCS_model


wald1 <- 
  summary_InCS_model$CoefTable[3]^2 /
  summary_InCS_model$CoefTable[7]^2

wald2 <- 
  summary_InCS_model$CoefTable[4]^2 /
  summary_InCS_model$CoefTable[8]^2


summary_InCS_model
summary_InCS_model$coefficients[3]
data.frame(exp(InCSModel$coefficients))

exp(InCSModel$coefficients)[3]


a <- exp(confint(InCSModel))
c(a[3],a[7])

residuals(InCSModel)
fitted(InCSModel, outcome = F)

c <- summary_InCS_model$lratio$statistic
w <- sqrt(c/length(df3$gender))
pw <- pwr.chisq.test(w=w,N=length(df3$InCS),df=(2),sig.level = .05)

pw$power

revised_PseudoR2s <- function(LogModel) {
  dev <- LogModel$deviance
  nullDev <- LogModel$null.deviance
  modelN <- length(LogModel$fitted.values)
  R.l <- 1 - dev / nullDev
  R.cs <- 1- exp ( -(nullDev - dev) / modelN)
  R.n <- R.cs / ( 1 - ( exp (-(nullDev / modelN))))
  
  all <- list(hosmer_and_lemeshow = as.numeric(R.l), mcfadden = NA, cox_and_snell = as.numeric(R.cs), nagelkerke = as.numeric(R.n))
  all
}

logits_rsquared <- glm(InCS~NFC,df3, family = binomial(link = "logit"))
cox <- revised_PseudoR2s(logits_rsquared)


```


A multinomial logistic regression revealed no significant association between Need for Cognition and response to the critical slide, $\chi$^2^(`r summary_InCS_model$lratio$parameter`, *N* = `r length(df3$gender)`) = `r round(summary_InCS_model$lratio$statistic, digits=2)`, *p* `r paste(p_report(summary_InCS_model$lratio$p.value))`, the observed power was `r round(pw$power,digits=2)` (see Figure\ \@ref(fig:S2ggplotlogit2) for relative probabilities of selecting each response depending on Need for Cognition).

